---
title: "Dear Enemy"
author: "Joshua Manning"
date: "`r Sys.Date()`"
output: html_document
---

Load packages

```{r}
#Data wrangling
library(plyr)
library(dplyr) 
library(tidyr) 
library(tibble) 
library(lubridate) #Dealing with time issues

#Movement and spatial analyses
library(adehabitatHR) #Home range analyses
library(adehabitatLT)
library(sf)  #Simple features
library(sp)  #This will be retired soon, but the code using sp objects can be shifted to sf objects easily enough
library(nngeo) #For function st_remove_holes

#Statistical analyses
library(car) #ANOVA
library(glmmTMB) #For linear, generalized linear, and generalized linear mixed modeling
library(performance)
library(DHARMa) #Checking model assumptions
library(emmeans) #marginal means of mixed models

#Data visualization
library(ggplot2) #Tidyverse visualization package
library(ggpubr) #For ggarrange() etc.
library(extrafont) #Change plot fonts

#Misc
library(conflicted) #Resolved conflicts
```

Resolve conflicts

```{r}
conflict_prefer("rename", "dplyr")
conflict_prefer("group_by", "dplyr")
conflict_prefer("filter", "dplyr")
conflict_prefer("summarise", "dplyr")
conflict_prefer("select", "dplyr")
conflict_prefer("mutate", "dplyr")
conflict_prefer("count", "dplyr")
conflict_prefer("contr.sum", "stats")
conflict_prefer("id", "adehabitatLT")
```




##Load dear enemy observations and benthic data

```{r}
dear <- read.csv("Data/dearenemy.csv")

benthic.annot <- read.csv("Data/Annotations.csv")
benthic.label <- read.csv("Data/Labelset.csv")
``` 


#Clean dear enemy dataset and prepare for analyses

We made observations of interactions between focal terminal phase (TP) S. viride and both TP and initial phase (IP) conspecifics. Our focus here is on TP-TP interactions. So, I will subset the data.
```{r}
tp <- dear %>%
  filter(Int.Phase == "TP")

ip <- dear %>%
  filter(Int.Phase == "IP")
```


#Clean benthic dataset and prepare for analyses

```{r}
benthic.lab <- benthic.label %>%
  select(-c(Label.ID)) %>%
  rename(Label = Short.Code)

benthic <- benthic.annot %>%
  select(-c(Aux5:White.balance.card, Row, Column)) %>%
  left_join(benthic.lab)
```

Let's get it summarized by quadrat. 
1. Count labels at quadrat level, by functional group
2. Remove Unknowns, Shadow, and Quadrat points
3. Combine CCA, CCA_Turf, and Turf
4. Combine Macroalgae and Pavement_Macroalgae
5. Combine all rubble columns
6. Summarize number of known points per quadrat
7. Divide all columns by number of known points
8. Gather to long format to do transect level analyses for sites and for territories

```{r}
benthic.quad <- benthic %>%
  select(-Label) %>%
  group_by(Site, Territory, Transect, Quadrat, Functional) %>%
  summarise(N = n()) %>%
  spread(Functional, N) %>%
  mutate(across(everything(), ~replace_na(.x, 0))) %>%
  select(-c(Shadow, Tape, Unk)) %>% #remove Unknowns, Shadow, and Quadrat annotations
  mutate(Turf_CCA = CCA + CCA_Turf + Turf,
         Macro = Macroalgae + Pavement_Macroalgae,
         Rubbles = Rubble + Rubble_CCA + Rubble_Turf + Rubble_Turf_Sediment) %>%
  select(-c(CCA, CCA_Turf, Turf, 
            Macroalgae, Pavement_Macroalgae, 
            Rubble, Rubble_CCA, Rubble_Turf, Rubble_Turf_Sediment)) %>%
  ungroup() %>%
  mutate(Sum = rowSums(select(.,ArtCA:Rubbles))) %>%
  mutate(across(c(ArtCA:Rubbles), .fns = ~./Sum*100)) %>%
  mutate(TotalCover = rowSums(select(.,ArtCA:Rubbles))) %>% #check that %cover adds to 100, it does
  select(-c(Sum, TotalCover)) %>%
  gather(Substrates, Cover, ArtCA:Rubbles)
```

Summarize at transect level

```{r}
benthic.trans <- benthic.quad %>%
  group_by(Site, Territory, Transect, Substrates) %>%
  summarise(MeanT = mean(Cover)) %>%
  unite(ID, Site:Territory, sep = "_", remove = F)
```


##Analysis of differences in the cover of epilithic turf and crustose coralline algae between territories and sites.

```{r}
tcca <- benthic.trans %>% 
  filter(Substrates == "Turf_CCA")

m.tcca <- lm(MeanT ~ Site*Territory, data = tcca)
par(mfrow = c(2,2))
plot(m.tcca)
par(mfrow = c(1,1))
Anova(m.tcca)
```
Anova Table (Type II tests)

Response: MeanT
               Sum Sq Df F value  Pr(>F)  
Site            468.2  1  4.9861 0.03186 *
Territory        32.9  1  0.3502 0.55770  
Site:Territory    9.8  1  0.1048 0.74805  
Residuals      3380.6 36                  
---
Signif. codes:  0 ‘***’ 0.001 ‘**’ 0.01 ‘*’ 0.05 ‘.’ 0.1 ‘ ’ 1


#Plots of site and territory level resource abundance

```{r}
benthic.sites <- benthic.trans %>%
  group_by(Site, Substrates) %>%
  summarise(N = n(),
            Mean = mean(MeanT),
            SE = sd(MeanT)/sqrt(N))

tcca.sites <- benthic.sites %>%
  filter(Substrates == "Turf_CCA")

tcca.box.site <- benthic.sites %>% 
  filter(Substrates == "Turf_CCA") %>%
  ggplot(aes(y = Mean, x = Site, fill = Site))  + 
  geom_bar(stat="identity", color="black", position=position_dodge()) +
  geom_errorbar(aes(ymin = Mean - SE, ymax = Mean + SE), width=0, position=position_dodge(.9)) +
  labs(y = "% Cover", x = "Territory") +
  theme_classic()
tcca.box.site

benthic.terr <- benthic.trans %>%
  group_by(Site, Territory, Substrates) %>%
  summarise(N = n(),
            Mean = mean(MeanT),
            SE = sd(MeanT)/sqrt(N)) %>%
  unite(Territory, c(Site, Territory), remove = T)

tcca.terr <- benthic.terr %>%
  filter(Substrates == "Turf_CCA") %>%
  select(Territory, Mean) %>%
  rename(TCCA = Mean)

tcca.box.terr <- benthic.terr %>% 
  filter(Substrates == "Turf_CCA") %>%
  separate(Territory, c("Site", "Territory"), sep = "_") %>%
  ggplot(aes(y = Mean, x = Territory, fill = Site))  + 
  geom_bar(stat="identity", color="black", position=position_dodge()) +
  geom_errorbar(aes(ymin = Mean - SE, ymax = Mean + SE), width=0, position=position_dodge(.9)) +
  labs(y = "% Cover", x = "Territory") +
  theme_classic()
tcca.box.terr
```




##Analyses of TP S. viride intraspecific interactions with other TP S. viride

Prep data and do some basic statistics
```{r}
#Subset to include only agonistic interactions and exclude non-interactions
tp2 <- tp %>%
  filter(Interact == "Y") %>%
  unite("Territory", c("Site", "Terr.Num"), remove = F) %>%
  mutate(Intensity = ifelse(Chase == "Y", "High", "Low")) %>%
  mutate(across(Duration, round)) %>% #round to the nearest second
  left_join(tcca.terr) %>%
  mutate(Chase.Bi = as.numeric(ifelse(Chase == "Y", "1", "0")))

#Subset for non-interactions
tp.n <- tp %>%
  filter(Interact == "N") %>%
  unite("Territory", c("Site", "Terr.Num"), remove = F)

#Summarize number of interactions with neighbors and floaters for each individual
tpcounts <- tp2 %>%
  group_by(Territory, F.Size, Harem, TCCA, Int.Type) %>%
  summarise(N = n()) %>%
  spread(Int.Type, N) %>%
  mutate(across(everything(), ~replace_na(.x, 0))) %>%
  gather(Int.Type, N, Floater:Neighbor)

#Summarize the relative sizes of interactors
int.sizes <- tp2 %>%
  group_by(Int.Type, Int.Size) %>%
  summarise(N = n())
int.sizes

#Calculate mean and standard deviation of focal parrotfish sizes
focal.sizes <- tp2 %>%
  group_by(Territory) %>%
  summarise(Size = round(max(F.Size))) %>%
  summarise(SL = mean(Size),
            sdSL = sd(Size))
focal.sizes
```

Analyze interaction frequencies

```{r}
#Initial visualization
count.box <- ggplot(data = tpcounts, aes(y = N, x = Int.Type)) +
  geom_boxplot(outlier.shape = 4, size = 0.25, position = position_dodge2(preserve = "single"), alpha = 0.9) +
  geom_point(position=position_dodge2(width = 0.1), colour = "black", size = 1) +
  labs(y = "Number of Interactions", x = "Relationship") +
  theme_classic(base_family = "Arial") +
  theme(legend.position = "none",
        axis.title = element_text(size = 12, color = "black"),
        axis.text = element_text(size = 10, color = "black"))
count.box

#Model
count.final <- tpcounts %>%
  separate(Territory, c("Site", "Rep"), sep = "_")

count.p <-glmmTMB(data = count.final, N ~ Site + Int.Type, family = poisson)

test.count.p <- simulateResiduals(fittedModel = count.p, n = 250, plot = T) #Normal and there is no heteroscedasticity
plotResiduals(test.count.p) #looks good
testDispersion(test.count.p) #meets dispersion assumptions
testOutliers(test.count.p) #outlier test is not significant

#Stats
summary(count.p)

glmm.count.ANOVA <- Anova(count.p)
glmm.count.ANOVA
```
Analysis of Deviance Table (Type II Wald chisquare tests)
Response: N
          Chisq Df Pr(>Chisq)
Site     1.9729  1     0.1601
Int.Type 0.7165  1     0.3973


Interaction Durations

```{r}
#Initial visualization
length.box <- ggplot(data = tp2, aes(y = Duration, x = Int.Type)) +
  geom_boxplot(outlier.shape = 4, size = 0.25, position = position_dodge2(preserve = "single"), alpha=0.9) +
  geom_point(size = 1) +
  labs(y = "Interaction Duration (s)", x = "Relationship") +
  scale_color_manual(values = c("black", "white")) +
  theme_classic() +
  theme(legend.position = "none",
        axis.title = element_text(size = 12, color = "black"),
        axis.text = element_text(size = 10, color = "black"))
length.box


#Check the three outliers
check <- tp2 %>%
  filter(Duration > 50)

#For later, identify the outliers
tp3 <- tp2 %>%
  mutate(Outlier = ifelse(Duration > 50, "Y", "N"))


#Duration of Interactions
dur.glm <- glmmTMB(data = tp2, log(Duration) ~ Site + Int.Type + (1|Site:Territory), family = "gaussian")

test.dur.glm <- simulateResiduals(fittedModel = dur.glm, n = 250, plot = T) #Normal and there is no heteroscedasticity
plotResiduals(test.dur.glm) #looks good
testDispersion(test.dur.glm) #meets dispersion assumptions
testOutliers(test.dur.glm) #outlier test is not significant

#Stats
summary(dur.glm)

glmm.int.dur.anova <- Anova(dur.glm, type = 2)
glmm.int.dur.anova
```
Family: gaussian  ( identity )
Formula:          log(Duration) ~ Site + Int.Type + (1 | Site:Territory)
Data: tp2

     AIC      BIC   logLik deviance df.resid 
   130.0    139.6    -60.0    120.0       45 

Random effects:

Conditional model:
 Groups         Name        Variance Std.Dev.
 Site:Territory (Intercept) 0.1256   0.3544  
 Residual                   0.5575   0.7466  
Number of obs: 50, groups:  Site:Territory, 10

Dispersion estimate for gaussian family (sigma^2): 0.557 

Conditional model:
                 Estimate Std. Error z value Pr(>|z|)    
(Intercept)       2.87888    0.27880  10.326   <2e-16 ***
SiteIV           -0.15010    0.31989  -0.469    0.639    
Int.TypeNeighbor -0.08674    0.24243  -0.358    0.720    
---
Signif. codes:  0 ‘***’ 0.001 ‘**’ 0.01 ‘*’ 0.05 ‘.’ 0.1 ‘ ’ 1


Analysis of Deviance Table (Type II Wald chisquare tests)

Response: log(Duration)
          Chisq Df Pr(>Chisq)
Site     0.2202  1     0.6389
Int.Type 0.1280  1     0.7205


#Plot frequency of interactions and interaction durations in a two panel plot

```{r}
#Calculate the total number of interactions with neighbors and floaters to add to plot/captions
sum.int.total <- tp3 %>%
  group_by(Int.Type) %>%
  summarise(N = n())
sum.int.total

#Re-plot interaction frequency
count.box2 <- ggplot(data = tpcounts,aes(y = N,x = Int.Type)) +
  geom_boxplot(outlier.shape = 4, size = 0.25, position = position_dodge2(preserve = "single"), alpha = 0.9) +
  geom_point(position=position_dodge2(width = 0.1), colour = "black", size = 1.5, alpha = 0.5) +
  labs(y = "Number of Interactions", x = "Relationship") +
  theme_classic(base_family = "Arial") +
  theme(legend.position = "none",
        axis.title = element_text(size = 12, color = "black"),
        axis.text = element_text(size = 10, color = "black"))
count.box2

#Re-plot interaction durations
length.box2 <- ggplot(data = tp3, aes(y = Duration, x = Int.Type)) +
  geom_boxplot(outlier.shape = 4, size = 0.25, position = position_dodge2(preserve = "single"), alpha=0.9) +
  geom_point(aes(color = Outlier), position = position_dodge2(width = 0.1), size = 1.5, alpha = 0.5) +
  labs(y = "Interaction Duration (s)", x = "Relationship") +
  scale_color_manual(values = c("black", "white")) +
  theme_classic() +
  theme(legend.position = "none",
        axis.title = element_text(size = 12, color = "black"),
        axis.text = element_text(size = 10, color = "black"))
length.box2

dee.p <- ggarrange(count.box2 + rremove("xlab") + rremove("x.text"), length.box2,
                     labels = c("a", "b"),
                     ncol = 1, nrow = 2, align = "v",
                     font.label = list(size = 12, color = "black", face = "plain", family = "Arial"))
dee.p

#Save figure
ggsave("Figures/DearEnemy/FigureS1_DearEnemy.png", plot = dee.p,
       width = 3.25, height = 5, dpi = 300)
```


#Analysis of interaction intensities

```{r}
#Summarize the number of interactions between neighbors and floaters that were either highly aggressive or not
intensity.sum <- tp2 %>%
  mutate(across(c(Territory, Int.Type, Intensity), as.factor)) %>%
  group_by(Territory, Int.Type, Intensity, .drop = F) %>%
  summarise(N = n())
intensity.sum


#Quick look at the intensities
count.intensity = ggplot(data = intensity.sum, aes(y = N, x = Int.Type)) +
  geom_boxplot(aes(color = Intensity), outlier.shape = 4, size=1, alpha=0.9) +
  geom_point(position=position_jitterdodge(jitter.width = 0.1), aes(fill = Intensity), 
             colour = "black", pch = 21, alpha = 0.6, size = 3) +
  labs(y = "Number of Interactions", x = "Relationship") +
  theme_classic()
count.intensity


#Intensity of Interactions Analysis
Intensity <- tp2 %>%
  group_by(Int.Type, Intensity) %>%
  summarise(N = n(),
            mDuration = mean(Duration),
            seDuration = sd(Duration)/sqrt(N))
Intensity


#Create a contingency table to do the Fisher's Exact test with
IntensityInTenCities <- table(tp2$Int.Type, tp2$Intensity)
IntensityInTenCities

fisher.test(IntensityInTenCities) #p = 0.007

#Check out high intensity interactions among neighbors to try to find out why
intenseneighbors <- tp2 %>%
  filter(Int.Type == "Neighbor" & Intensity == "High")

#Take a look at resource holding potential (RHP), here relative size, of neighbors and floaters
RHP <- table(tp2$Int.Type, tp2$Int.Size)
RHP

#Chase Probability
intense.glm <- glmmTMB(data = tp2, Chase.Bi ~ Site + Int.Type + (1|Site:Territory), family = "binomial")

test.intense.glm <- simulateResiduals(fittedModel = intense.glm, n = 250, plot = T) #looks good
plotResiduals(test.intense.glm) #looks good
testDispersion(test.intense.glm) #meets dispersion assumptions
testOutliers(test.intense.glm) #outlier test is not significant

#Stats
summary(intense.glm)

glmm.intense.anova <- Anova(intense.glm, type = 2)
glmm.intense.anova

fixef(intense.glm)
confint(intense.glm)

#marginal means for significant factors

emm.intense.type <- emmeans(intense.glm, ~Int.Type, type = "response")
emm.intense.sum <- summary(emm.intense.type)


emm.intense.p <- ggplot(emm.intense.sum, aes(x = Int.Type, y = prob)) +
  geom_jitter(data = tp2, aes(x = Int.Type, y = Chase.Bi), width = 0.25, height = 0, color = "gray45") +
  geom_point(size = 3) +
  geom_errorbar(aes(ymin = asymp.LCL, ymax = asymp.UCL, group=Int.Type), width = 0) +
  theme_classic() +
  theme(axis.title = element_text(size = 12, color = "black"),
        axis.text = element_text(size = 10, color = "black"),
        axis.title.x = element_blank(),
        axis.text.x = element_text(color = "black"),
        legend.position = "none") +
  labs(x = "", y = "Chase Probability")
emm.intense.p

ggsave("Figures/DearEnemy/Figure2_DearEnemy.png", plot = emm.intense.p,
       width = 3.25, height = 4, dpi = 300)
```

Fisher's Exact Test for Count Data

data:  IntensityInTenCities
p-value = 0.006529
alternative hypothesis: true odds ratio is not equal to 1
95 percent confidence interval:
   1.686234 706.332956
sample estimates:
odds ratio 
   14.6328 


GLMM of the probability of chase occurring as a function of site and interactor identity (neighbor v. stranger) with random effects
Family: binomial  ( logit )
Formula:          Chase.Bi ~ Site + Int.Type + (1 | Site:Territory)
Data: tp2

     AIC      BIC   logLik deviance df.resid 
    45.2     52.8    -18.6     37.2       46 

Random effects:

Conditional model:
 Groups         Name        Variance Std.Dev.
 Site:Territory (Intercept) 0.0303   0.1741  
Number of obs: 50, groups:  Site:Territory, 10

Conditional model:
                 Estimate Std. Error z value Pr(>|z|)  
(Intercept)        3.0313     1.2506   2.424   0.0154 *
SiteIV             0.4586     0.8336   0.550   0.5822  
Int.TypeNeighbor  -2.6880     1.1989  -2.242   0.0250 *
---
Signif. codes:  0 ‘***’ 0.001 ‘**’ 0.01 ‘*’ 0.05 ‘.’ 0.1 ‘ ’ 1


Analysis of Deviance Table (Type II Wald chisquare tests)
Response: Chase.Bi
          Chisq Df Pr(>Chisq)  
Site     0.3027  1    0.58222  
Int.Type 5.0265  1    0.02496 *
---
Signif. codes:  0 ‘***’ 0.001 ‘**’ 0.01 ‘*’ 0.05 ‘.’ 0.1 ‘ ’ 1



##Take a look at home ranges, buffer zones, and the movement paths of floaters at Invisibles

Read in the full movement dataset and shapefiles from concurrently conducted study: ADD DRYAD INFO HERE.

```{r}
move <- read.csv("Data/move2021.csv")

ivHR <- st_read("ProcessedData/iv2021.mkde95.shp") 
```

1. For Invisibles, subset just the S. viride tracks analyzed in the other manuscript: tracks after June 1, 2021. 
2. Create a subset for the other tracks of S. viride from before June 1, 2021

```{r}
ivHR.spv <- ivHR %>%
  filter(Species == "Spviride",
         Phase == "TP",
         Date > "2021-06-01")

ivHR.spvPRE <- ivHR %>%
  filter(Species == "Spviride",
         Phase == "TP",
         Date < "2021-06-01")
``` 

1. Remove holes from center of computed boundaries of home ranges. These holes are likely just artifacts given the strong territorial behavior of these fish. 
2. Create a 2.95 m buffer for each home range, reflecting the mean distance that TP-TP S. viride interactions occur from the home range boundary.

```{r}
iv.buffers <-ivHR.spv %>%
  st_remove_holes() %>%
  st_buffer(dist = -2.95)
```

Separate out the two opportunistic floater tracks

```{r}
conflict_prefer("summarize", "dplyr")

#Figure out which individuals are floaters and subset the data to include only those relocations
iv.spv.float <- move %>%
  separate(ID, c("Site", "Species", "Phase", "Date", "EndTime"), sep = "_", remove = F) %>%
  filter(Site == "IV",
         Species == "Spviride",
         Phase == "NTP") %>% 
  slice(-c(134:138)) %>% #cut off relocations after I lost the 1st floater in the video (at 10:38:29)
  st_as_sf(coords = c("lon", "lat")) %>% #create sf object
  group_by(ID) %>%
  summarise(do_union=FALSE) %>%
  st_cast("LINESTRING") #create linestring sf
  
st_crs(iv.spv.float) = 4326
iv.spv.float <- st_transform(iv.spv.float, crs = 32619)

#For 1st floater, subset track into phases where it is being chased or not chased.
iv.spv.float.1 <- move %>%
  separate(ID, c("Site", "Species", "Phase", "Date", "EndTime"), sep = "_", remove = F) %>%
  filter(Site == "IV",
         Species == "Spviride",
         Phase == "NTP",
         Date == '2021-05-22') %>%
  slice(-c(1:103,106:138)) %>% #1st chase of floater 1
  st_as_sf(coords = c("lon", "lat")) %>%
  group_by(ID) %>%
  summarise(do_union=FALSE) %>%
  st_cast("LINESTRING")

st_crs(iv.spv.float.1) = 4326
iv.spv.float.1 <- st_transform(iv.spv.float.1, crs = 32619)
  
iv.spv.float.2 <- move %>%
  separate(ID, c("Site", "Species", "Phase", "Date", "EndTime"), sep = "_", remove = F) %>%
  filter(Site == "IV",
         Species == "Spviride",
         Phase == "NTP",
         Date == '2021-05-22') %>%
  slice(-c(1:114,118:138)) %>% #2nd chase of floater 1, expanded to include relocs just outside to create line.
  st_as_sf(coords = c("lon", "lat")) %>%
  group_by(ID) %>%
  summarise(do_union=FALSE) %>%
  st_cast("LINESTRING")

st_crs(iv.spv.float.2) = 4326
iv.spv.float.2 <- st_transform(iv.spv.float.2, crs = 32619)  
  
iv.spv.float.3 <- move %>%
  separate(ID, c("Site", "Species", "Phase", "Date", "EndTime"), sep = "_", remove = F) %>%
  filter(Site == "IV",
         Species == "Spviride",
         Phase == "NTP",
         Date == '2021-05-22') %>%
  slice(-c(1:117, 134:138)) %>% #subset for third floater chase, removing relocs at end after I had lost visual in video.
  st_as_sf(coords = c("lon", "lat")) %>%
  group_by(ID) %>%
  summarise(do_union=FALSE) %>%
  st_cast("LINESTRING")

st_crs(iv.spv.float.3) = 4326
iv.spv.float.3 <- st_transform(iv.spv.float.3, crs = 32619)   

IV.spv.floaters <- ggplot() +
  geom_sf(data = ivHR.spv, inherit.aes = FALSE, linewidth = 1,
          fill = "gray 45", alpha = 0.75, color = "black") +   #plot home ranges as calculated in other manuscript
  geom_sf(data = iv.buffers, inherit.aes = FALSE, linewidth = 1, 
          fill = "gray 95", alpha = 0.75, color = "black", lty = "dashed") + #plot buffers for those home ranges
  geom_sf(data = iv.spv.float, aes(color = ID), linewidth = 2) + #plot both floaters
  geom_sf(data = iv.spv.float.1, color="black", linewidth = 2) + #overlay black for areas 1st was being chased
  geom_sf(data = iv.spv.float.2, color="black", linewidth = 2) + #overlay black for areas 1st was being chased
  geom_sf(data = iv.spv.float.3, color="black", linewidth = 2) + #overlay black for areas 1st was being chased
  coord_sf(datum = st_crs(32619)) +
  scale_x_continuous(breaks = c(578140, 578175, 578210)) +
  scale_y_continuous(breaks = c(1335260, 1335300, 1335340)) +
  labs(x = "Easting", y = "Northing") +
  theme_classic() +
  theme(text=element_text(family = "Arial"),
        axis.text = element_text(size = 10),
        panel.border = element_rect(colour = "black", fill=NA, linewidth=2),
        legend.position = "none")
IV.spv.floaters
```
This is good, but we have tracks for other territorial TP S. viride and replicate tracks for some of these that could fill out this map better. So, we will do that.


##Compute home ranges for S. viride using all replicate GPS tracks

First we need to determine which tracks are replicates that we can combine. We will do this visually.
```{r}
#Plot tracks from May
IV.spv.PRE <- ggplot() +
  geom_sf(data = ivHR.spvPRE, aes(fill = ID),inherit.aes = FALSE, linewidth = 1, alpha = 0.75, color = "black") +
  coord_sf(datum = st_crs(32619)) +
  scale_x_continuous(limits = c(578135, 578215), breaks = c(578140, 578175, 578210)) +
  scale_y_continuous(limits = c(1335210, 1335350), breaks = c(1335220, 1335260, 1335300, 1335340)) +
  labs(x = "Easting", y = "Northing") +
  theme_classic() +
  theme(text=element_text(family = "Arial"),
        axis.text = element_text(size = 10),
        panel.border = element_rect(colour = "black", fill=NA, linewidth = 2))
IV.spv.PRE

#Plot tracks from July
IV.spv.POST <- ggplot() +
  geom_sf(data = ivHR.spv, aes(fill = ID),inherit.aes = FALSE, linewidth = 1, alpha = 0.75, color = "black") +
  coord_sf(datum = st_crs(32619)) +
  scale_x_continuous(limits = c(578135, 578215), breaks = c(578140, 578175, 578210)) +
  scale_y_continuous(limits = c(1335210, 1335350), breaks = c(1335220, 1335260, 1335300, 1335340)) +
  labs(x = "Easting", y = "Northing") +
  theme_classic() +
  theme(text=element_text(family = "Arial"),
        axis.text = element_text(size = 10),
        panel.border = element_rect(colour = "black", fill=NA, linewidth = 2))
IV.spv.POST
```
Compare these plots do determine which tracks are replicate tracks to merge for home range computation.


##Calculate new S. viride home ranges incorporating all tracks for the fish at IV

1. Start with the full movement dataset.
2. Because the time column has more than just the date and time (i.e., T and Z), separate into multiple columns and then unite the two columns without those characters. This makes it easier later...
3. Sort out replicates and provide those tracks with identifiers.

```{r}
#separate the column in two at the T
movings <- move %>% separate(time, c("Date","Time"), sep = c("T")) 

movings$Time = substr(movings$Time,1,nchar(movings$Time)-1) ##remove last character (in this case the Z)

#Unite time and separate the ID and filter so I only have TP Sp. viride at IV. 
movings2 <- unite(movings, "time", c(Date, Time), sep = " ", remove=T) %>%
  separate(ID, c("Site", "Species", "Phase", "Date", "End"), sep = "_") %>%
  separate(End, c("EndTime", "file"), sep = "[.]") %>%
  select(-file) %>%
  filter(Site == "IV", 
         Species == "Spviride", 
         Phase == "TP") %>%
  filter(!(Date == "2021-05-22" & EndTime == "111618"), #Remove this one, strange territory (is it?) and south of area
         !(Date == "2021-05-22" & EndTime == "132756")) #Remove replicate of one territory w/a big tail (interaction?) 

tnames <- movings2 %>%
  select(-c(lon:time)) %>%
  unique()

#Add territory names based on maps of territories in May and July from above. If territories are overlapping, they are likely the same individuals.
tnames$Territory <- c("T1", "T2", "T4", "T5", "T3", "T4", "T9", "T8", "T1", "T7", "T2", "T3", "T4", "T5", "T6")

moving <- full_join(movings2, tnames)
```

4. Next, create a trajectory object. First, convert it to a SpatialPointsDataFrame. Using the coordinates function will create a SPDF. The CRS can be set using CRS("+proj=longlat +ellps=WGS84 +datum=WGS84 +no_defs") or CRS(SRS_string="EPSG:4326"). The latter is preferred in the new system.

```{r}
loc <- data.frame("x" = moving$lon, "y" = moving$lat)
proj4string = CRS(SRS_string="EPSG:4326")
proj4string

moving.spdf <- SpatialPointsDataFrame(loc, moving, proj4string = proj4string)
```

5. Convert CRS to UTM Zone 19 EPSG: 32619 for projection in Bonaire. Units in meters.

```{r}
moving.spdf.met = spTransform(moving.spdf, 
                              CRS(SRS_string="EPSG:32619"))

str(moving.spdf.met) #check
```

6. Next, create an ltraj object. This is a Type 2 trajectory, with time recorded. The time needs to be of class POSIXct object in order to convert to ltraj. Convert time to POSIXct.

```{r}
moving.spdf.met$time <- as.POSIXct(strptime(as.character(moving.spdf.met$time), "%Y-%m-%d %H:%M:%S"))

class(moving.spdf.met$time)
```

7. Now I can create the ltraj object: The resulting object belongs to the classes ltraj and list. It is a list of dataframes that should behave like any other list in R.

```{r}
raw_tracks <- as.ltraj(coordinates(moving.spdf.met), date = moving.spdf.met$time, id=moving.spdf.met$Territory, typeII = T)

class(raw_tracks)
```

8. Do some summaries

```{r}
length(raw_tracks)
```
9 unique tracks

Calculate mean, min, max, the time and distance between relocations
```{r}
traj_df <- ld(raw_tracks)
str(traj_df)
traj_df$id <- as.factor(traj_df$id)

traj_summary <- traj_df %>%
  select(-burst, -pkey) %>%
  group_by(id) %>%
  summarise(tmu = mean(dt, na.rm = T),
            tmax = max(dt, na.rm = T),
            tmin = min(dt, na.rm = T),
            dmu = mean(dist, na.rm = T),
            dmax = max(dist, na.rm = T),
            dmin = min(dist, na.rm = T),
            N = n(),
            totaltime = sum(dt, na.rm = T)/60)
traj_summary

traj_summary2 <- as.data.frame(traj_summary)
```
These look crazy for the 5 fish we have replicate tracks for... but it makes sense.


#Compute home range and core use areas of merged tracks using movement-based kernel density estimation. 

Specify the parameters for the MKDE Brownian Bridge model. Calculate vv for each track with Tmax = 60 s and Lmin = 0 m.

```{r}
ivvv <- BRB.D(raw_tracks, Tmax = 60, Lmin = 0)

median(do.call(rbind.data.frame, ivvv)$D) #0.11

hmin <- 1
```

Estimate UD, used the diffusion parameter 

```{r}
ivud <- BRB(raw_tracks, D = ivvv, Tmax = 60, Lmin = 0, hmin=hmin, filtershort = F, grid = 300, same4all = T)

conflict_prefer("id", "adehabitatLT")
names(ivud) <- id(raw_tracks)
```

Get the home range contours. Remove the holes in the home range and calculate the buffers. The holes are likely artifacts of home range estimation, so we will plot without them.

```{r}
iv.ud95 <- getverticeshr(ivud, percent = 95, unin = "m", unout = "m2")

proj4string(iv.ud95) <- CRS(SRS_string="EPSG:32619") #add the UTM projection CRS to match the data

#Convert to sf object using st_as_sf in the sf package
iv.mkde95 <- st_as_sf(iv.ud95) %>%
  rownames_to_column(var = "Territory") %>%
  st_set_crs(32619) %>%
  st_remove_holes()

iv.mkde95.whole <- st_as_sf(iv.ud95) %>%
  rownames_to_column(var = "Territory") %>%
  st_set_crs(32619)

#Create buffers after removing holes from home ranges (to avoid making buffers around holes, which may be artefacts)
iv.buffers2 <-iv.mkde95 %>%
  st_remove_holes() %>%
  st_buffer(dist = -2.95)
```

Plot new HRs

"#0072B2" "#D55E00"

```{r}
IV.spv.floaters2 <- ggplot() +
  geom_sf(data = iv.mkde95.whole, inherit.aes = FALSE, size = 0.5, fill = "gray 95", alpha = 0.45, color = "black") +
  geom_sf(data = iv.buffers2, inherit.aes = FALSE, size = 0.5, fill = "gray 45", alpha = 0.45, color = "black", lty = "dashed") +
  geom_sf(data = iv.spv.float, color = c("#0072B2", "#D55E00"), size = 1, alpha = 0.75) +
  geom_sf(data = iv.spv.float.1, color="maroon", size = 1) +
  geom_sf(data = iv.spv.float.2, color="maroon", size = 1) +
  geom_sf(data = iv.spv.float.3, color="maroon", size = 1) +
  coord_sf(datum = st_crs(32619)) +
  scale_x_continuous(breaks = c(578140, 578175, 578210)) +
  scale_y_continuous(breaks = c(1335260, 1335300, 1335340)) +
  labs(x = "Easting (m)", y = "Northing (m)") +
  theme_classic(base_family = "Arial") +
  theme(axis.text = element_text(size = 10, color = "black"),
        axis.title = element_text(size = 12, color = "black"),
        panel.border = element_rect(colour = "black", fill=NA, size=2),
        legend.position = "none")
IV.spv.floaters2

ggsave("Figures/DearEnemy/Figure3_DearEnemy.png", plot = IV.spv.floaters2,
       width = 3.25, height = 5, dpi = 300)
```