---
title: "DynamicInteractions"
author: "Joshua Manning"
date: "`r Sys.Date()`"
output: html_document
---

Load packages
Not all are used. Some are remnants of prior coding and more packages may be added later.

```{r}
#Reading in, handling, cleaning data.

library(plotKML) #function in this package for loading GPX files.
library(tidyr) #data handling
library(plyr)
library(dplyr) #data wrangling
library(tibble)
library(lubridate)

#Movement and spatial analyses

library(sf)
library(sp)
library(raster)

library(adehabitatLT)
library(adehabitatHR) #analyses of home ranges and other movement code
library(wildlifeDI) #for dynamic interaction analyses

#Statistical analyses

library(car) #Anova() function
library(glmmTMB) #generalized linear mixed models
library(MuMIn) #dredge() function for model selection
library(DHARMa) #assumption checking
library(performance) #assumption checking
library(emmeans) #marginal means estimation
library(multcomp) #post-hoc multiple comparisons

#Plotting and mapping

library(ggplot2) #visualization
library(ggpubr) #for ggarrange() etc.
library(gridExtra) #has a function for comparing ggplot plots side by side.
library(RColorBrewer) #nice palettes

library(ggmap) #use this for plotting maps
#library(ggmapstyles) #to use premade mapstyles from snazzy maps
library(ggsn) #to add scale bars and north arrow
library(ggspatial) #add scale bar and north arrow
library(maps)
library(mapdata)
library(rworldmap)
library(maptools)

#Dealing with conflicts

library(conflicted)
```

Resolve conflicts

```{r}
conflict_prefer("rename", "dplyr")
conflict_prefer("group_by", "dplyr")
conflict_prefer("filter", "dplyr")
conflict_prefer("summarise", "dplyr")
conflict_prefer("select", "dplyr")
conflict_prefer("mutate", "dplyr")
conflict_prefer("count", "dplyr")
conflict_prefer("contr.sum", "stats")
conflict_prefer("id", "adehabitatLT")
```

Species color scheme for plots

```{r}
sci.color <- "#542788"
sct.color <- "#FCBBA1"
scv.color <- "#F768A1"
spa.color <- "#980043"
spv.color <- "#35978F"

sp.color.all <- c(sci.color, sct.color, scv.color, spa.color, spv.color)
mainsp.color <- c(sct.color, scv.color, spa.color, spv.color)
```




##Start on dynamic interactions using the simultaneous tracks

Read in the data from simultaneous GPS tracks

```{r}
dynamic <- read.csv("Data/dynamic.csv")

##separate the column in two at the T
dynamical <- dynamic %>% separate(time, c("Date","Time"), sep = c("T"))
dynamical$Time = substr(dynamical$Time,1,nchar(dynamical$Time)-1) ##remove last character (in this case the Z)

dynamics <- unite(dynamical, "time", c(Date, Time), sep = " ", remove=T) %>%
  separate(ID, c("Type", "Replicate", "Site", "Foc.Species", "Foc.Phase", "Int.Species", "Int.Phase", "Date", "EndTime"), sep = "_") %>%
  select(-c(8,9,12)) %>% #remove unnecessary columns
  filter(!(Foc.Species == Int.Species & Foc.Phase == Int.Phase)) %>% ##removes TP-intraspecific dynamic tracks that I won't be analyzing
  mutate(Int.Type = ifelse(Foc.Species != Int.Species, "Interspecific", "Intraspecific")) %>% #adds column for type of interaction
  unite(Int.ID, c("Site", "Int.Type", "Type", "Replicate"), sep = "_")

#Separate into two datasets for the focal fish (TP Sp. viride) and the interactors (TP Sc. vetula and IP Sp. viride)
dyn.foc <- dynamics %>%
  filter(Foc.Species == "Spviride" & Foc.Phase == "TP") %>%
  unite(id, c("Int.ID", "Foc.Species", "Foc.Phase", "Int.Species", "Int.Phase"), sep = ".")

dyn.int <- dynamics %>%
  filter(!(Foc.Species == "Spviride" & Foc.Phase == "TP")) %>%
  unite(id, c("Int.ID", "Foc.Species", "Foc.Phase", "Int.Species", "Int.Phase"), sep = ".")
```

Create a trajectory object.

First, convert it to a SpatialPointsDataFrame. CRS can be set using CRS("+proj=longlat +ellps=WGS84 +datum=WGS84 +no_defs") or CRS(SRS_string="EPSG:4326"). The latter is preferred.

```{r}
proj4string = CRS(SRS_string="EPSG:4326") #use EPSG:4326 because this is the format the GPS receiver records data in
proj4string

loc.foc <- data.frame("x" = dyn.foc$lon, "y" = dyn.foc$lat)
loc.int <- data.frame("x" = dyn.int$lon, "y" = dyn.int$lat)

dyn.foc.spdf <- SpatialPointsDataFrame(loc.foc, dyn.foc, proj4string = proj4string)
dyn.int.spdf <- SpatialPointsDataFrame(loc.int, dyn.int, proj4string = proj4string)
```

Convert CRS to UTM Zone 19 EPSG: 32619 for projection in Bonaire. Units in meters.

```{r}
dyn.foc.spdf <- spTransform(dyn.foc.spdf, CRS(SRS_string="EPSG:32619"))
dyn.int.spdf <- spTransform(dyn.int.spdf, CRS(SRS_string="EPSG:32619"))

str(dyn.foc.spdf)
```

Next, create the ltraj object. This is a Type 2 trajectory, with time recorded. The time needs to be converted to class POSIXct in order to convert to ltraj.

```{r}
dyn.foc.spdf$time <- as.POSIXct(strptime(as.character(dyn.foc.spdf$time), "%Y-%m-%d %H:%M:%S"))
dyn.int.spdf$time <- as.POSIXct(strptime(as.character(dyn.int.spdf$time), "%Y-%m-%d %H:%M:%S"))

class(dyn.foc.spdf$time)
```

Create the ltraj object:

The resulting object belongs to the classes ltraj and list. It is a list of dataframes that should behave like any other list in R.

```{r}
dyn.foc.tr <- as.ltraj(coordinates(dyn.foc.spdf), date = dyn.foc.spdf$time, id=dyn.foc.spdf$id, typeII = T)
dyn.int.tr <- as.ltraj(coordinates(dyn.int.spdf), date = dyn.int.spdf$time, id=dyn.int.spdf$id, typeII = T)

dyn.foc.tr
```


#Summarize trajectory information for these fish

```{r}
dyn.foc.tr.df <- ld(dyn.foc.tr)
dyn.foc.tr.df$id <- as.factor(dyn.foc.tr.df$id)

dyn.int.tr.df <- ld(dyn.int.tr)
dyn.int.tr.df$id <- as.factor(dyn.int.tr.df$id)

dyn.tr.df <- rbind(dyn.foc.tr.df, dyn.int.tr.df)

#Summarise for interspecific dynamic interactions
int.dyn.tr.sum <- dyn.tr.df %>%
  select(-burst, -pkey) %>%
  group_by(id) %>%
  summarise(tmu = mean(dt, na.rm = T),
            dmu = mean(dist, na.rm = T),
            n = n(),
            totaltime = sum(dt, na.rm = T)/60) %>%
  separate(id, c("Int.ID", "Foc.Species", "Foc.Phase", "Int.Species", "Int.Phase"), sep = "[.]") %>%
  filter(Int.ID != "AQ_Intraspecific_DI_03") %>%  #remove pair that did not overlap
  separate(Int.ID, c("Site", "PairType", "Type", "Rep"), sep = "_") %>%
  filter(PairType != "Intraspecific") %>%
  summarise(N = n(),
            mTBR = mean(tmu),
            sdTBR = sd(tmu),
            seTBR = sdTBR/sqrt(N),
            mDBR = mean(dmu),
            sdDBR = sd(dmu),
            seDBR = sdDBR/sqrt(N),
            mRelocations = mean(n),
            sdRelocations = sd(n),
            seRelocations = sdRelocations/sqrt(N),
            mTime = mean(totaltime),
            sdTime = sd(totaltime),
            seTime = sdTime/sqrt(N))
int.dyn.tr.sum

dyn.tr.sum.all <- dyn.tr.df %>%
  select(-burst, -pkey) %>%
  group_by(id) %>%
  summarise(tmu = mean(dt, na.rm = T),
            dmu = mean(dist, na.rm = T),
            n = n(),
            totaltime = sum(dt, na.rm = T)/60) %>%
  separate(id, c("Int.ID", "Foc.Species", "Foc.Phase", "Int.Species", "Int.Phase"), sep = "[.]") %>%
  filter(Int.ID != "AQ_Intraspecific_DI_03") %>%  #remove pair that did not overlap
  separate(Int.ID, c("Site", "PairType", "Type", "Rep"), sep = "_") %>%
  group_by(PairType, Foc.Species, Foc.Phase) %>%
  summarise(N = n(),
            mRelocations = mean(n),
            sdRelocations = sd(n),
            mTime = mean(totaltime),
            sdTime = sd(totaltime)) %>%
  mutate(across(mRelocations:sdTime, round, 2)) %>% 
  unite("Mean (SD) Relocations", mRelocations:sdRelocations, sep = " \u00B1 ") %>% 
  unite("Mean (SD) Time (min)", mTime:sdTime, sep = " \u00B1 ")
dyn.tr.sum.all

write.table(dyn.tr.sum.all, file = "DataSummary/StaticDynamic/dyn.tr.sum.all.txt",
            sep = ",", quote = FALSE, row.names = F)
```
Track summary for all individuals in interspecific pairs of simultaneously tracked parrotfishes

      N  mTBR sdTBR seTBR  mDBR sdDBR seDBR mRelocations sdRelocations seRelocations mTime sdTime seTime
  <int> <dbl> <dbl> <dbl> <dbl> <dbl> <dbl>        <dbl>         <dbl>         <dbl> <dbl>  <dbl>  <dbl>
1    18  10.8  2.06 0.486  2.16 0.453 0.107         180.          32.5          7.67  31.2   2.00  0.472


#Computation of home ranges of fish tracked simultaneously

Create an SPDF for each site. 

```{r}
aq.dyn <- dynamics %>%
  unite(ID, c("Int.ID", "Foc.Species", "Foc.Phase", "Int.Species", "Int.Phase"), sep = ".") %>%
  filter(!grepl("IV", ID))

iv.dyn <- dynamics %>%
  unite(ID, c("Int.ID", "Foc.Species", "Foc.Phase", "Int.Species", "Int.Phase"), sep = ".") %>%
  filter(!grepl("AQ", ID))


aq.dyn.loc <- data.frame("x" = aq.dyn$lon, "y" = aq.dyn$lat)
iv.dyn.loc <- data.frame("x" = iv.dyn$lon, "y" = iv.dyn$lat)


aq.dyn.spdf <- SpatialPointsDataFrame(aq.dyn.loc, aq.dyn, proj4string = proj4string)
aq.dyn.spdf = spTransform(aq.dyn.spdf, CRS(SRS_string="EPSG:32619")) #convert CRS to UTM Zone 19 EPSG: 32619 for projection in Bonaire

iv.dyn.spdf <- SpatialPointsDataFrame(iv.dyn.loc, iv.dyn, proj4string = proj4string)
iv.dyn.spdf = spTransform(iv.dyn.spdf, CRS(SRS_string="EPSG:32619")) #convert CRS to UTM Zone 19 EPSG: 32619 for projection in Bonaire
```

Create a type II ltraj object, but first convert time to POSIXct.

```{r}
aq.dyn.spdf$time <- as.POSIXct(strptime(as.character(aq.dyn.spdf$time), "%Y-%m-%d %H:%M:%S"))
iv.dyn.spdf$time <- as.POSIXct(strptime(as.character(iv.dyn.spdf$time), "%Y-%m-%d %H:%M:%S"))

str(aq.dyn.spdf) #check to see that time is POSIXct... it is.
```

Now create the ltraj object:
The resulting object belongs to the classes ltraj and list. It is a list of dataframes that should behave like any other list.

```{r}
aq.dyn.t <- as.ltraj(coordinates(aq.dyn.spdf), date = aq.dyn.spdf$time, id=aq.dyn.spdf$ID, typeII = T)
iv.dyn.t <- as.ltraj(coordinates(iv.dyn.spdf), date = iv.dyn.spdf$time, id=iv.dyn.spdf$ID, typeII = T)
```

Specify the parameters for the MKDE Brownian Bridge model. Calculate vv for each track/site specifying Tmax as 60 s and Lmin to 0 m. Set hmin = 1.

```{r}
aq.dyn.vv <- BRB.D(aq.dyn.t, Tmax = 60, Lmin = 0)
iv.dyn.vv <- BRB.D(iv.dyn.t, Tmax = 60, Lmin = 0)

median(do.call(rbind.data.frame, aq.dyn.vv)$D) #0.08
median(do.call(rbind.data.frame, iv.dyn.vv)$D) #0.07

hmin <- 1
```

Estimate UD, using the diffusion parameter

```{r}
aq.dyn.ud <- BRB(aq.dyn.t, D = aq.dyn.vv, Tmax = 60, Lmin = 0, hmin=hmin, filtershort = F, grid = 300, same4all = T)
iv.dyn.ud <- BRB(iv.dyn.t, D = iv.dyn.vv, Tmax = 60, Lmin = 0, hmin=hmin, filtershort = F, grid = 300, same4all = T)

conflict_prefer("id", "adehabitatLT")
names(aq.dyn.ud) <- id(aq.dyn.t)
names(iv.dyn.ud) <- id(iv.dyn.t)
```

Estimate areas

```{r}
aq.dyn.95 <- kernel.area(aq.dyn.ud, percent = 95, unin = "m", unout = "m2")
iv.dyn.95 <- kernel.area(iv.dyn.ud, percent = 95, unin = "m", unout = "m2")
```

Merge area dataframes

```{r}
dyn.area.mkde.95 <- cbind(aq.dyn.95, iv.dyn.95)

dyn.area.mkde.95l <- pivot_longer(dyn.area.mkde.95, cols = c(1:ncol(dyn.area.mkde.95)), names_to = "id", values_to = "area.mkde.95")

dyn.area.mkde <- dyn.area.mkde.95l %>% 
  separate(id, c("Int.ID", "Foc.Species", "Foc.Phase", "Int.Species", "Int.Phase"), sep = "[.]")

write.csv(dyn.area.mkde, "ProcessedData/Dynamic_HRs.csv", row.names = F)
```

Summarise

```{r}
dyn.mkde.sum <- dyn.area.mkde %>%
  filter(Int.ID != "AQ_Intraspecific_DI_03") %>%                            #remove pair that did not overlap
  separate(Int.ID, c("Site", "PairType", "Type", "Rep"), sep = "_") %>%
  group_by(PairType, Foc.Species, Foc.Phase) %>%
  summarise(N = n(),
            mHR = mean(area.mkde.95),
            sdHR = sd(area.mkde.95)) %>%
  mutate(across(mHR:sdHR, round, 2)) %>% 
  unite("HR", mHR:sdHR, sep = " \u00B1 ")
dyn.mkde.sum

write.table(dyn.mkde.sum, file = "DataSummary/StaticDynamic/dynamic.HR.txt",
            sep = ",", quote = FALSE, row.names = F)
```


#Compute spatial overlap of pairs of simultaneously tracked home ranges and core areas using 'kerneloverlaphr' in adehabitatHR package. I used Bhattacharyya's Affinity as my metric. 

```{r}
aq.dyn.BA <- kerneloverlaphr(aq.dyn.ud, method = "BA", conditional = T, percent = 95)
iv.dyn.BA <- kerneloverlaphr(iv.dyn.ud, method = "BA", conditional = T, percent = 95)
```

Now, let's clean up these dataframes

```{r}
#rownames to column
aq.dyn.BA2 <- tibble::rownames_to_column(as.data.frame(aq.dyn.BA), "id1")
iv.dyn.BA2 <- tibble::rownames_to_column(as.data.frame(iv.dyn.BA), "id1")

#convert to long format
aq.dyn.BA.l <- pivot_longer(aq.dyn.BA2, cols = c(2:ncol(aq.dyn.BA2)), names_to = "id2", values_to = "BA")
iv.dyn.BA.l <- pivot_longer(iv.dyn.BA2, cols = c(2:ncol(iv.dyn.BA2)), names_to = "id2", values_to = "BA")

#bind site data sets
dyn.overlap.BA <- as.data.frame(rbind(aq.dyn.BA.l, iv.dyn.BA.l))
dyn.overlap.BA$BA <- dyn.overlap.BA$BA/0.95 #divide by 0.95 to make the proportions between 0 and 1

#organize by pairs
dyn.overlap.pairs.BA <- dyn.overlap.BA %>%
  separate(id1, c("ID1", "Foc.Species1", "Foc.Phase1", "Int.Species1", "Int.Phase1"), sep = "[.]") %>%
  unite(Pair1, Foc.Species1:Int.Phase1, sep = "_") %>%
  separate(id2, c("ID2", "Foc.Species2", "Foc.Phase2", "Int.Species2", "Int.Phase2"), sep = "[.]") %>%
  unite(Pair2, Foc.Species2:Int.Phase2, sep = "_") %>%
  filter(ID1 == ID2 & Pair1 != Pair2)

#create final dataset for each by removing duplicates (reciprocal)
dyn.overlap.final.BA <- dyn.overlap.pairs.BA[!duplicated(t(apply(dyn.overlap.pairs.BA, 1, sort))), ] %>%
  select(-Pair1, -ID2) %>%
  separate(ID1, c("Site", "PairType", "Type", "Rep"), sep = "_")

#do some summarizing
sum.dyn.overlap.BA <- dyn.overlap.final.BA %>%
  filter(BA != 0) %>%
  group_by(PairType) %>%
  summarise(N = n(),
            mBA = mean(BA),
            seBA = sd(BA)/sqrt(N)) %>%
  mutate(across(mBA:seBA, round, 2)) %>% 
  unite("BA", mBA:seBA, sep = " \u00B1 ")
sum.dyn.overlap.BA

write.table(sum.dyn.overlap.BA, file = "ProcessedData/dynamic.overlap.BA.txt",
            sep = ",", quote = FALSE, row.names = F)
```


#Compute probability of simultaneously tracked individuals being found each other's home ranges and core areas using 'kerneloverlaphr' in adehabitatHR package.

```{r}
aq.dyn.PHR95 <- kerneloverlaphr(aq.dyn.ud, method = "PHR", conditional = T, percent = 95)
iv.dyn.PHR95 <- kerneloverlaphr(iv.dyn.ud, method = "PHR", conditional = T, percent = 95)

aq.dyn.PHR50 <- kerneloverlaphr(aq.dyn.ud, method = "PHR", conditional = T, percent = 50)
iv.dyn.PHR50 <- kerneloverlaphr(iv.dyn.ud, method = "PHR", conditional = T, percent = 50)
```

Clean up these dataframes

```{r}
#rownames to column
aq.dyn.PHR95.2 <- tibble::rownames_to_column(as.data.frame(aq.dyn.PHR95), "id1")
iv.dyn.PHR95.2 <- tibble::rownames_to_column(as.data.frame(iv.dyn.PHR95), "id1")

aq.dyn.PHR50.2 <- tibble::rownames_to_column(as.data.frame(aq.dyn.PHR50), "id1")
iv.dyn.PHR50.2 <- tibble::rownames_to_column(as.data.frame(iv.dyn.PHR50), "id1")

#convert to long format
aq.dyn.PHR95.l <- pivot_longer(aq.dyn.PHR95.2, cols = c(2:ncol(aq.dyn.PHR95.2)), names_to = "id2", values_to = "PHR")
iv.dyn.PHR95.l <- pivot_longer(iv.dyn.PHR95.2, cols = c(2:ncol(iv.dyn.PHR95.2)), names_to = "id2", values_to = "PHR")

aq.dyn.PHR50.l <- pivot_longer(aq.dyn.PHR50.2, cols = c(2:ncol(aq.dyn.PHR50.2)), names_to = "id2", values_to = "PHR")
iv.dyn.PHR50.l <- pivot_longer(iv.dyn.PHR50.2, cols = c(2:ncol(iv.dyn.PHR50.2)), names_to = "id2", values_to = "PHR")

#bind site data sets
dyn.overlap.PHR95 <- as.data.frame(rbind(aq.dyn.PHR95.l, iv.dyn.PHR95.l))

dyn.overlap.PHR50 <- as.data.frame(rbind(aq.dyn.PHR50.l, iv.dyn.PHR50.l))


#organize by pairs
dyn.overlap.pairs.PHR95 <- dyn.overlap.PHR95 %>%
  separate(id1, c("ID1", "Foc.Species1", "Foc.Phase1", "Int.Species1", "Int.Phase1"), sep = "[.]") %>%
  unite(Pair1, Foc.Species1:Int.Phase1, sep = "_") %>%
  separate(id2, c("ID2", "Foc.Species2", "Foc.Phase2", "Int.Species2", "Int.Phase2"), sep = "[.]") %>%
  unite(Pair2, Foc.Species2:Int.Phase2, sep = "_") %>%
  filter(ID1 == ID2 & Pair1 != Pair2)

dyn.overlap.pairs.PHR50 <- dyn.overlap.PHR50 %>%
  separate(id1, c("ID1", "Foc.Species1", "Foc.Phase1", "Int.Species1", "Int.Phase1"), sep = "[.]") %>%
  unite(Pair1, Foc.Species1:Int.Phase1, sep = "_") %>%
  separate(id2, c("ID2", "Foc.Species2", "Foc.Phase2", "Int.Species2", "Int.Phase2"), sep = "[.]") %>%
  unite(Pair2, Foc.Species2:Int.Phase2, sep = "_") %>%
  filter(ID1 == ID2 & Pair1 != Pair2)

#create final dataset for each after removing the pair with no overlap ("AQ_Intraspecific_DI_03")
dyn.overlap.final.PHR95 <- dyn.overlap.pairs.PHR95 %>%
  filter(ID1 != "AQ_Intraspecific_DI_03") %>%
  select(-Pair1, -ID2) %>%
  separate(ID1, c("Site", "PairType", "Type", "Rep"), sep = "_")

dyn.overlap.final.PHR50 <- dyn.overlap.pairs.PHR50 %>%
  filter(ID1 != "AQ_Intraspecific_DI_03") %>%
  select(-Pair1, -ID2) %>%
  separate(ID1, c("Site", "PairType", "Type", "Rep"), sep = "_")

#merge HR and CA overlaps into one dataset for the Appendix
dyn.overlap.final.PHR <- dyn.overlap.final.PHR95 %>%
  rename(PHR95 = "PHR") %>%
  full_join(dyn.overlap.final.PHR50) %>%
  rename(PHR50 = "PHR")

dyn.overlap.final.PHR

write.table(dyn.overlap.final.PHR, file = "ProcessedData/dynamic.overlap.final.PHR.txt",
            sep = ",", quote = FALSE, row.names = F)

inter.dyn.overlap.final.PHR <- dyn.overlap.final.PHR %>% filter(PairType == "Interspecific")
inter.dyn.overlap.final.PHR
```


#Dynamic Interaction Analyses

Rediscretize tracks to improve the likelihood of obtaining points to use for dynamic interaction analyses. Here, we implemented a time rediscritization using the redisltraj function in the adehabitatLT package, to generate relocations every second for each individual.

```{r}
dyn.foc.rd <- redisltraj(dyn.foc.tr, u = 1, samplex0 = F, type = "time")
dyn.int.rd <- redisltraj(dyn.int.tr, u = 1, samplex0 = F, type = "time")
```

Use the `GetSimultaneous` function in the `wildlifeDI` package to find simultaneous fixes, and then keep every 5th location in the final data set.

```{r}
sim <- GetSimultaneous(dyn.foc.rd, dyn.int.rd, tc = 0)
```

```{r}
sim.df <- ld(sim) %>%
  select(-c(4:10)) %>%
  separate(id, c("Int.ID", "Foc.Species", "Foc.Phase", "Int.Species", "Int.Phase"), sep = "[.]") %>%
  select(-c("burst", "pkey"))  %>%
  group_by(Int.ID, Foc.Species, Foc.Phase, Int.Species, Int.Phase) %>%
  filter(row_number() %% 5 == 1) ##keeps every 5th location
```

```{r}
sim.sum <- sim.df %>%
  group_by(Int.ID, Foc.Species, Foc.Phase) %>%
  summarise(N = n(),
            Start = min(date),
            End = max(date)) %>%
  filter(Int.ID != "AQ_Intraspecific_DI_03") %>%                            #remove pair that did not overlap
  separate(Int.ID, c("Site", "PairType", "Type", "Rep"), sep = "_") %>%
  group_by(PairType, Foc.Species, Foc.Phase) %>%
  summarise(n = n(),
            mSim = mean(N),
            sdSim = sd(N),
            seSim = sdSim/sqrt(n))
sim.sum

sim.sf <- st_as_sf(sim.df, coords = c("x", "y"), crs = 32619)
```

Create sf objects of the home range contours for mapping and for determining shared areas using the MKDE UDs from above

```{r}
#First I use getvertices in the adehabitatHR package to get the countours for the home ranges I computed.

dyn.aq.ud95 <- getverticeshr(aq.dyn.ud, percent = 95, unin = "m", unout = "m2")
dyn.iv.ud95 <- getverticeshr(iv.dyn.ud, percent = 95, unin = "m", unout = "m2")

dyn.aq.ud50 <- getverticeshr(aq.dyn.ud, percent = 50, unin = "m", unout = "m2")
dyn.iv.ud50 <- getverticeshr(iv.dyn.ud, percent = 50, unin = "m", unout = "m2")

#Now I generate the shapefiles

#AQ
proj4string(dyn.aq.ud95) <- CRS(SRS_string="EPSG:32619") #add the UTM projection CRS to match the data
proj4string(dyn.aq.ud50) <- CRS(SRS_string="EPSG:32619")

#Convert to sf object using st_as_sf in the sf package
dyn.aq.mkde95 <- st_as_sf(dyn.aq.ud95) %>%
  separate(id, c("Int.ID", "Foc.Species", "Foc.Phase", "Int.Species", "Int.Phase"), sep = "[.]") %>%
  rownames_to_column(var = "ID") %>%
  mutate(ID = gsub('[.]', '_', ID))

st_write(dyn.aq.mkde95, "ProcessedData/dyn.aq2021.mkde95.shp", append = F)

dyn.aq.mkde50 <- st_as_sf(dyn.aq.ud50) %>%
  separate(id, c("Int.ID", "Foc.Species", "Foc.Phase", "Int.Species", "Int.Phase"), sep = "[.]") %>%
  rownames_to_column(var = "ID") %>%
  mutate(ID = gsub('[.]', '_', ID))

st_write(dyn.aq.mkde50, "ProcessedData/dyn.aq2021.mkde50.shp", append = F)

#IV
proj4string(dyn.iv.ud95) <- CRS(SRS_string="EPSG:32619")
proj4string(dyn.iv.ud50) <- CRS(SRS_string="EPSG:32619")

#Convert to sf object using st_as_sf in the sf package
dyn.iv.mkde95 <- st_as_sf(dyn.iv.ud95) %>%
  separate(id, c("Int.ID", "Foc.Species", "Foc.Phase", "Int.Species", "Int.Phase"), sep = "[.]") %>%
  rownames_to_column(var = "ID") %>%
  mutate(ID = gsub('[.]', '_', ID))

st_write(dyn.iv.mkde95, "ProcessedData/dyn.iv2021.mkde95.shp", append = F)

dyn.iv.mkde50 <- st_as_sf(dyn.iv.ud50) %>%
  separate(id, c("Int.ID", "Foc.Species", "Foc.Phase", "Int.Species", "Int.Phase"), sep = "[.]") %>%
  rownames_to_column(var = "ID") %>%
  mutate(ID = gsub('[.]', '_', ID))

st_write(dyn.iv.mkde50, "ProcessedData/dyn.iv2021.mkde50.shp", append = F)
```

Now I need to determine the intersecting areas of pairs of home ranges from dynamic tracks.

```{r}
aq.ovlp <- st_intersection(dyn.aq.mkde95, dyn.aq.mkde95) %>%
  filter(Int.ID == Int.ID.1,
         Int.Species == Int.Species.1 & Int.Phase != Int.Phase.1 | Int.Species != Int.Species.1 & Int.Phase == Int.Phase.1) %>%
  group_by(grp = paste(pmax(ID, ID.1), pmin(ID, ID.1), sep = "-")) %>%
  slice(1) %>%
  ungroup() %>%
  select(-c(7:14,16))


iv.ovlp <- st_intersection(dyn.iv.mkde95, dyn.iv.mkde95) %>%
  filter(Int.ID == Int.ID.1,
         Int.Species == Int.Species.1 & Int.Phase != Int.Phase.1 | Int.Species != Int.Species.1 & Int.Phase == Int.Phase.1) %>%
  group_by(grp = paste(pmax(ID, ID.1), pmin(ID, ID.1), sep = "-")) %>%
  slice(1) %>%
  ungroup() %>%
  select(-c(7:14,16))
```

Now let's determine which locations are within each of these areas

```{r}
library(data.table) #for transpose()

aq.sim.sf <- sim.sf %>% filter(!grepl("IV", Int.ID))

aq.intersects <- as.data.frame(st_intersects(aq.ovlp, aq.sim.sf, sparse = F), row.names = aq.ovlp$Int.ID)
aq.intersects.t <- transpose(aq.intersects)
colnames(aq.intersects.t) <- rownames(aq.intersects)

aq.sim.x <- cbind(aq.sim.sf, aq.intersects.t) %>%
  gather(key = "Ovlp.ID", value = "Ovlp", AQ_Interspecific_DI_01:AQ_Intraspecific_DI_05) %>%
  filter(Int.ID == Ovlp.ID)

#I lost some data (722 observations after this last step... So, somewhere, the Int.ID and Ovlp.ID didn't match...). Let's find out why...
aq.sim.sf.sum <- aq.sim.sf %>%
  group_by(Int.ID, Foc.Species, Foc.Phase) %>%
  summarise(N = n())
aq.sim.sf.sum

aq.sim.x.sum <- aq.sim.x %>%
  group_by(Int.ID, Foc.Species, Foc.Phase) %>%
  summarise(N = n())
aq.sim.x.sum
#The AQ_Intraspecific_DI_03 pair was removed, because there was no overlap between their home ranges.


iv.sim.sf <- sim.sf %>% filter(!grepl("AQ", Int.ID))

iv.intersects <- as.data.frame(st_intersects(iv.ovlp, iv.sim.sf, sparse = F), row.names = iv.ovlp$Int.ID)
iv.intersects.t <- transpose(iv.intersects)
colnames(iv.intersects.t) <- rownames(iv.intersects)

iv.sim.x <- cbind(iv.sim.sf, iv.intersects.t) %>%
  gather(key = "Ovlp.ID", value = "Ovlp", IV_Interspecific_DI_01:IV_Intraspecific_DI_05) %>%
  filter(Int.ID == Ovlp.ID)

iv.sim.x.sum <- iv.sim.x %>%
  group_by(Int.ID, Foc.Species, Foc.Phase) %>%
  summarise(N = n())
```

Now that I have information on whether locations overlap the shared area, I can create dataframes that allow me to do the dynamic interaction analyses

```{r}
conflict_prefer("arrange", "dplyr")

aq.sim.x.foc <- aq.sim.x %>%
  mutate(lon = st_coordinates(.)[,1],
         lat = st_coordinates(.)[,2]) %>%
  st_drop_geometry() %>%
  filter(Foc.Species == "Spviride" & Foc.Phase == "TP") %>%
  unite(Foc.ID, c("Foc.Species", "Foc.Phase", "Int.Species", "Int.Phase"), sep = "_") %>%
  select(-Ovlp.ID) %>%
  group_by(Int.ID) %>% 
  mutate(SimLoc = row_number()) %>%
  ungroup()

aq.sim.x.int <- aq.sim.x %>%
  mutate(lon = st_coordinates(.)[,1],
         lat = st_coordinates(.)[,2]) %>%
  st_drop_geometry() %>%
  filter(!(Foc.Species == "Spviride" & Foc.Phase == "TP")) %>%
  unite(Foc.ID, c("Foc.Species", "Foc.Phase", "Int.Species", "Int.Phase"), sep = "_") %>%
  select(-Ovlp.ID) %>%
  group_by(Int.ID) %>% 
  mutate(SimLoc = row_number()) %>%
  ungroup()

aq.final <- merge(aq.sim.x.foc, aq.sim.x.int, by = c("Int.ID","SimLoc")) %>%
  arrange(Int.ID, SimLoc) %>%
  rename(F.Date = date.x,
         F.ID = Foc.ID.x,
         F.Ovlp = Ovlp.x,
         F.lon = lon.x,
         F.lat = lat.x,
         I.Date = date.y,
         I.ID = Foc.ID.y,
         I.Ovlp = Ovlp.y,
         I.lon = lon.y,
         I.lat = lat.y) %>%
  relocate(F.Ovlp, .before = I.Ovlp)


iv.sim.x.foc <- iv.sim.x %>%
  mutate(lon = st_coordinates(.)[,1],
         lat = st_coordinates(.)[,2]) %>%
  st_drop_geometry() %>%
  filter(Foc.Species == "Spviride" & Foc.Phase == "TP") %>%
  unite(Foc.ID, c("Foc.Species", "Foc.Phase", "Int.Species", "Int.Phase"), sep = "_") %>%
  select(-Ovlp.ID) %>%
  group_by(Int.ID) %>% 
  mutate(SimLoc = row_number()) %>%
  ungroup()
  
iv.sim.x.int <- iv.sim.x %>%
  mutate(lon = st_coordinates(.)[,1],
         lat = st_coordinates(.)[,2]) %>%
  st_drop_geometry() %>%
  filter(!(Foc.Species == "Spviride" & Foc.Phase == "TP")) %>%
  unite(Foc.ID, c("Foc.Species", "Foc.Phase", "Int.Species", "Int.Phase"), sep = "_") %>%
  select(-Ovlp.ID) %>%
  group_by(Int.ID) %>% 
  mutate(SimLoc = row_number()) %>%
  ungroup()

iv.final <- merge(iv.sim.x.foc, iv.sim.x.int, by = c("Int.ID","SimLoc")) %>%
  arrange(Int.ID, SimLoc) %>%
  rename(F.Date = date.x,
         F.ID = Foc.ID.x,
         F.Ovlp = Ovlp.x,
         F.lon = lon.x,
         F.lat = lat.x,
         I.Date = date.y,
         I.ID = Foc.ID.y,
         I.Ovlp = Ovlp.y,
         I.lon = lon.y,
         I.lat = lat.y) %>%
  relocate(F.Ovlp, .before = I.Ovlp)


final <- rbind(aq.final, iv.final) %>%
  unite(F.I.Ovlp, c("F.Ovlp", "I.Ovlp"), sep = "-")
```


#Dynamic computations

Now I can summarise and start conduct analyses of dynamic interaction as described by Simon

Ns = Both in (TRUE-TRUE)
K = Foc in, Int out (TRUE-FALSE)
M = Foc out, Int in (FALSE-TRUE)
L = Both out (FALSE-FALSE)

```{r}
cummulative <- final %>%
  group_by(Int.ID, F.I.Ovlp) %>%
  summarise(N = n()) %>%
  spread(F.I.Ovlp, N) %>%
  rename(Ns = `TRUE-TRUE`,
         K = `TRUE-FALSE`,
         M = `FALSE-TRUE`,
         L = `FALSE-FALSE`) %>%
  mutate(Tot = Ns + K + M + L,
         Obs = Ns/Tot,
         Theo = ((Ns+K)/Tot)*((Ns+M)/Tot),
         Diff = Obs - Theo)
cummulative

Inter <- cummulative %>% filter(!grepl("Intraspecific", Int.ID))
Intra <- cummulative %>% filter(!grepl("Interspecific", Int.ID))

inter.dyn.test <- t.test(Inter$Obs, Inter$Theo, paired = T, conf.level = 0.95)
inter.dyn.test

inter.diff = Inter$Obs - Inter$Theo
hist(inter.diff,   
     col="gray", 
     main="Histogram of differences",
     xlab="Difference")

Inter.p <- Inter %>%
  gather(key = "Distribution", value = "Measurement", Obs:Theo) %>%
  group_by(Distribution) %>%
  summarise(N = n(),
            Mean = mean(Measurement),
            SE = sd(Measurement)/sqrt(N)) %>%
  ggplot() +
  geom_bar(aes(x = Distribution, y = Mean), stat = "identity", fill = "white", color = "black", linewidth = 0.5) +
  geom_errorbar(aes(x = Distribution, ymin = Mean - SE, ymax = Mean + SE), width = 0, size = 1, color = "black") +
  theme_classic() +
  scale_x_discrete(labels=c("Obs" = "Observed", "Theo" = "Theoretical")) +
  labs(x = "", title = "a. Interspecific") +
  theme(text = element_text(family = "Arial", color = "black"),
        axis.text.x = element_text(size = 12),
        axis.text.y = element_text(size = 10),
        axis.title = element_text(size = 12))
Inter.p

wilcox.test(Inter$Obs, Inter$Theo, paired = T) 


intra.dyn.test <- t.test(Intra$Obs, Intra$Theo, paired = T, conf.level = 0.95)
intra.dyn.test

intra.diff = Intra$Obs - Intra$Theo
hist(intra.diff,   
     col="gray", 
     main="Histogram of differences",
     xlab="Difference")

Intra.p <- Intra %>%
  gather(key = "Distribution", value = "Measurement", Obs:Theo) %>%
  group_by(Distribution) %>%
  summarise(N = n(),
            Mean = mean(Measurement),
            SE = sd(Measurement)/sqrt(N)) %>%
  ggplot() +
  geom_bar(aes(x = Distribution, y = Mean), stat = "identity", fill = "white", color = "black", linewidth = 0.5) +
  geom_errorbar(aes(x = Distribution, ymin = Mean - SE, ymax = Mean + SE), width = 0, size = 1, color = "black") +
  theme_classic() +
  scale_x_discrete(labels=c("Obs" = "Observed", "Theo" = "Theoretical")) +
  labs(x = "", title = "b. Intraspecific") +
  theme(text = element_text(family = "Arial", color = "black"),
        axis.text.x = element_text(size = 12),
        axis.text.y = element_text(size = 10),
        axis.title = element_text(size = 12))
Intra.p

wilcox.test(Intra$Obs, Intra$Theo, paired = T)

DI.p <- ggarrange(Inter.p, Intra.p,
                     labels = c("", ""),
                     ncol = 1, nrow = 2, align = "v")
DI.p
```

The frequency of simultaneous relocations of inter- and intraspecific pairs within shared areas did not differ from the frequency expected for independent movement. Therefore, despite significant static overlap, pairs of parrotfishes moved independently relative to the shared areas. We expected that there would be attraction among intraspecific pairs, both because transmission of social information among these individuals could increase successful identification of profitable foraging areas, or improve defense of haremic females (for TP Sp viride). We expected to see avoidance by interspecific pairs to limit interference competition and therefore allow for coexistence within shared areas. Now lets look at dynamic interaction in shared space.




##Truly Dynamic Interactions with IAB in wildlifeDI for relocations when both individuals were in shared areas. 

Create ltraj objects for the different interaction groups (TP Sp. viride)

```{r}
#Filter only locations in shared areas
ss.both <- final %>%
  filter(F.I.Ovlp == "TRUE-TRUE")

#Number of simultaneous locations within shared areas for each interaction pair.
ss.both.sum <- ss.both %>%
  group_by(Int.ID) %>%
  summarise(N = n())

#Subset for inter and intraspecific focal individuals
ss.inter.foc <- ss.both[,c(1,3:6)] %>%
  filter(!grepl("Intraspecific", Int.ID)) %>%
  rename(time = F.Date,
         ID = F.ID,
         lon = F.lon,
         lat = F.lat) %>%
  unite(ID.full, c("Int.ID", "ID"), sep = "_")

ss.intra.foc <- ss.both[,c(1,3:6)] %>%
  filter(!grepl("Interspecific", Int.ID)) %>%
  rename(time = F.Date,
         ID = F.ID,
         lon = F.lon,
         lat = F.lat) %>%
  unite(ID.full, c("Int.ID", "ID"), sep = "_")
  
#Subset for inter and intraspecific interacting individuals
ss.inter.int <- ss.both[,c(1,7:8,10:11)] %>%
  filter(!grepl("Intraspecific", Int.ID)) %>%
  rename(time = I.Date,
         ID = I.ID,
         lon = I.lon,
         lat = I.lat) %>%
  unite(ID.full, c("Int.ID", "ID"), sep = "_")

ss.intra.int <- ss.both[,c(1,7:8,10:11)] %>%
  filter(!grepl("Interspecific", Int.ID)) %>%
  rename(time = I.Date,
         ID = I.ID,
         lon = I.lon,
         lat = I.lat) %>%
  unite(ID.full, c("Int.ID", "ID"), sep = "_")
```

Now create ltraj objects
First make spdf

```{r}
proj4string2 = CRS(SRS_string="EPSG:32619")

#Focal TP Sp. viride

#Inter
simloc1 <- data.frame("x" = ss.inter.foc$lon, "y" = ss.inter.foc$lat)
inter.foc.spdf <- SpatialPointsDataFrame(simloc1, ss.inter.foc, proj4string = proj4string2)

#Intra
simloc2 <- data.frame("x" = ss.intra.foc$lon, "y" = ss.intra.foc$lat)
intra.foc.spdf <- SpatialPointsDataFrame(simloc2, ss.intra.foc, proj4string = proj4string2)


#Interacting TP Sc. vetula  and IP Sp. viride

#Inter
simloc3 <- data.frame("x" = ss.inter.int$lon, "y" = ss.inter.int$lat)
inter.int.spdf <- SpatialPointsDataFrame(simloc3, ss.inter.int, proj4string = proj4string2) 

#Intra
simloc4 <- data.frame("x" = ss.intra.int$lon, "y" = ss.intra.int$lat)
intra.int.spdf <- SpatialPointsDataFrame(simloc4, ss.intra.int, proj4string = proj4string2) 
```

Make sure time is right format.

```{r}
str(inter.foc.spdf)
```
They are in POSIXct.

Create the ltraj object.

```{r}
#Focal TP Sp. viride
#Inter
inter.foc.t <- as.ltraj(coordinates(inter.foc.spdf), date = inter.foc.spdf$time, id=inter.foc.spdf$ID.full, typeII = T)
#Intra
intra.foc.t <- as.ltraj(coordinates(intra.foc.spdf), date = intra.foc.spdf$time, id=intra.foc.spdf$ID.full, typeII = T)

#Interacting TP Sc. vetula and IP Sp.viride
#Inter
inter.int.t <- as.ltraj(coordinates(inter.int.spdf), date = inter.int.spdf$time, id=inter.int.spdf$ID.full, typeII = T)
#Intra
intra.int.t <- as.ltraj(coordinates(intra.int.spdf), date = intra.int.spdf$time, id=intra.int.spdf$ID.full, typeII = T)
```


##Global DI

```{r}
#Interspecific DI

inter.global <- list()

for(i in 1:9){
  out <- unlist(IAB(inter.foc.t[i], inter.int.t[i], tc = 0, dc = 10, rand = 99))
  inter.global[[i]] <- out

}

inter.global
inter.global.fin <- do.call(rbind.data.frame, inter.global)
inter.global.fin <- setNames(inter.global.fin, c("IAB.Obs", "IAB.Exp", "p.attract", "p.avoid"))
inter.global.fin$ID <- id(inter.foc.t)


write.table(inter.global.fin, "ProcessedData/InterspecificGlobalDI.txt", row.names = F)


#Intraspecific DI

intra.global <- list()

for(i in 1:9){
  out <- unlist(IAB(intra.foc.t[i], intra.int.t[i], tc = 0, dc = 10, rand = 99))
  intra.global[[i]] <- out

}

intra.global
intra.global.fin <- do.call(rbind.data.frame, intra.global)
intra.global.fin <- setNames(intra.global.fin, c("IAB.Obs", "IAB.Exp", "p.attract", "p.avoid"))
intra.global.fin$ID <- id(intra.foc.t)

write.table(intra.global.fin, "ProcessedData/IntraspecificGlobalDI.txt", row.names = F)
```

Make a table combining both the spatial overlap of each pair, with the dynamic interaction information.

```{r}
total.global.int <- rbind(inter.global.fin, intra.global.fin)

staticdynamic <- dyn.overlap.final.BA %>%
  unite(ID, c("Site", "PairType", "Type", "Rep", "Pair2"), sep = "_") %>%
  full_join(total.global.int) %>%
  filter(BA != 0) %>%
  separate(ID, c("Site", "PairType", "Type", "Rep", "Focal Species", "Focal Phase", 
                 "Interacting Species", "Interacting Phase"), sep = "_") %>%
  select(c(2,1,6,5,8,7,9:13)) %>%
  arrange(PairType) %>%
  unite(Focal, c("Focal Phase","Focal Species"), sep = " ") %>%
  unite(Interactor, c("Interacting Phase","Interacting Species"), sep = " ") %>%
  mutate(across(BA:p.avoid, round, 3))
staticdynamic

write.table(staticdynamic, "DataSummary/StaticDynamic/StaticDynamic.txt", 
            sep = ",", quote = FALSE, row.names = F)

inter.staticdynamic <- staticdynamic %>%
  filter(PairType == "Interspecific")
inter.staticdynamic
```


#Plot an interspecific dynamic tracks

This takes some time, so not necessary unless you want to rework for a different pair of individuals.

```{r}
library(moveVis)
library(move)
library(scales)

DI.movement <- dynamics %>%
  separate(Int.ID, c("Site", "Type", "Int", "Replicate"), sep = "_") 

DI.movement$time <- as.POSIXct(strptime(as.character(DI.movement$time), "%Y-%m-%d %H:%M:%S"))


##Interspecific Example

DI.AQ.Inter.04 <- DI.movement %>%
  filter(Site == "AQ" & Type == "Interspecific" & Replicate == "04")

DI.Inter.04 <- df2move(df = DI.AQ.Inter.04, proj = "+init=epsg:4326 +proj=longlat +datum=WGS84", x = "lon", y = "lat", 
                   time = "time", track_id = "Foc.Species")

DI.Inter.04p <- spTransform(DI.Inter.04, CRSobj="EPSG:32619")
projection(DI.Inter.04p)

m.Inter.04 <- align_move(DI.Inter.04p, res = "mean", unit = "secs", spaceMethod = "euclidean")

# create spatial frames with an OpenStreetMap
frames.Inter.04 <- frames_spatial(m.Inter.04, path_colours = c("#F768A1", "#35978F"),
                         map_service = "osm", alpha = 0.5) %>%
  add_labels(x = "Easting (m)", y = "Northing (m)") %>% # add some customizations, such as axis labels
  add_timestamps(m.Inter.04, type = "label")


frames.Inter.04.f <- add_gg(frames.Inter.04, expr(list(guides(color = guide_legend(title = "Species")),
                                   theme(legend.title = element_text(colour = "black", size=12)),
                                   geom_sf(data = dyn.aq.mkde50 %>% 
                                             filter(Int.ID == "AQ_Interspecific_DI_04" & Foc.Species == "Scvetula"),
                                           inherit.aes = FALSE, fill = NA, color = "#F768A1", linetype = "dashed"),
                                   geom_sf(data = dyn.aq.mkde95 %>% 
                                             filter(Int.ID == "AQ_Interspecific_DI_04" & Foc.Species == "Scvetula"),
                                           inherit.aes = FALSE, fill = NA, color = "#F768A1", linetype = "solid"),
                                   geom_sf(data = dyn.aq.mkde50 %>% 
                                             filter(Int.ID == "AQ_Interspecific_DI_04" & Foc.Species == "Spviride"),
                                           inherit.aes = FALSE, fill = NA, color = "#35978F", linetype = "dashed"),
                                   geom_sf(data = dyn.aq.mkde95 %>% 
                                             filter(Int.ID == "AQ_Interspecific_DI_04" & Foc.Species == "Spviride"),
                                           inherit.aes = FALSE, fill = NA, color = "#35978F", linetype = "solid"),
                                   coord_sf(datum = st_crs(32619)),
                                   scale_color_manual(labels = c(expression(italic("Scarus vetula")),
                                                                 expression(italic("Sparisoma viride"))),
                                                      values = c("#F768A1", "#35978F")),
                                   theme(plot.title = element_text(hjust = 0.5)),
                                   theme(axis.text = element_text(size = 10, color = "black")),
                                   theme(axis.title = element_text(size = 12, color = "black")),
                                   theme_classic(),
                                   theme(panel.border = element_rect(colour = "black", fill = NA, size=2)))))

                                   

frames.Inter.04.f[[100]] # preview one of the frames, e.g. the 100th frame

# animate frames
animate_frames(frames.Inter.04.f, out_file = "Figures/StaticDynamic/InterspecificDynamicInteractions.gif", overwrite = T)
```
