---
title: "Parasites"
author: "Joshua Manning"
date: "`r Sys.Date()`"
output: html_document
---

Load packages

```{r}
#Data wrangling
library(plyr)
library(dplyr) 
library(tidyr) 
library(tibble) 
library(lubridate) #Dealing with time issues

#Movement and spatial analyses
library(adehabitatHR) #Home range analyses
library(adehabitatLT)
library(sf)  #Simple features
library(sp)  #This will be retired soon, but the code using sp objects can be shifted to sf objects easily enough
library(nngeo) #For function st_remove_holes

#Statistical analyses
library(car) #ANOVA
library(glmmTMB) #For linear, generalized linear, and generalized linear mixed modeling
library(performance)
library(DHARMa) #Checking model assumptions
library(emmeans) #marginal means of mixed models

#Data visualization
library(ggplot2) #Tidyverse visualization package
library(ggpubr) #For ggarrange() etc.
library(extrafont) #Change plot fonts

#Misc
library(conflicted) #Resolved conflicts
```

Resolve conflicts

```{r}
conflict_prefer("rename", "dplyr")
conflict_prefer("group_by", "dplyr")
conflict_prefer("filter", "dplyr")
conflict_prefer("summarise", "dplyr")
conflict_prefer("select", "dplyr")
conflict_prefer("mutate", "dplyr")
conflict_prefer("count", "dplyr")
conflict_prefer("contr.sum", "stats")
conflict_prefer("id", "adehabitatLT")
conflict_prefer("icc", "irr")
```

Species colors

```{r}
sct.color <- "#FCBBA1"
spa.color <- "#980043"
```


## Load data

Read in standard lengths

```{r}
lengths <- read.csv("Data/stlength-harem.csv") %>%
  filter(Species %in% c("Sctaeniopterus", "Spaurofrenatum") & Phase == "TP") %>%
  # Sc taeniopterus - used male Sc taeniopterus fishbase - TL = 0 + 1.176*SL
  # Sp aurofrenatum - used male Sp viride fishbase - SL = 0 + 0.796*TL
  mutate(TL = ifelse(Species == "Sctaeniopterus", SL*1.176, SL/0.796),
  # Sc taeniopterus - used mixed Sc taeniopterus fishbase - FL = 0.968 + 1.160*SL
  # Sp aurofrenatum - used male Sp viride fishbase - FL = 0 + 0.894*TL
         FL = ifelse(Species == "Sctaeniopterus", (SL*1.160)+0.968, 0.894*TL)) %>%
  group_by(Species) %>%
  summarise(mSL = mean(SL),
            seSL = sd(SL)/sqrt(n()),
            mTotal_len = mean(TL), 
            seTotal_len = sd(TL)/sqrt(n()),
            mFL = mean(FL),
            seFL = sd(FL)/sqrt(n())) %>%
  ungroup()
```


Read in parasite data

```{r}
parasites <- read.csv("Data/parasites_total.csv") %>%
  separate(File.Name, c("Site", "Species", "Phase", "Date", "EndTime", "Vid"), sep = "_") %>%
  rename(BS1 = BS_Reviewer.1,
         BS2 = BS_Reviewer.2,
         WS1 = WS_Reviewer.1,
         WS2 = WS_Reviewer.2,
         BSr = Double_count_remove_BS) %>%
  select(-Body.Part) %>%
  # there were a few instances where two videos were used to count parasites. remove second video for now.
  group_by(Site, Species, Phase, Date, EndTime) %>%  # group by trial identifiers
  summarise(across(c(BS1:BSr), ~ round(mean(.x, na.rm = TRUE))),  # take mean of numeric columns
            Vid = paste(unique(Vid), collapse = ", ")) %>%  # optional: keep a record of which VIDs were combined
  ungroup() %>%
  select(-Vid) %>%
  # fill na with 0 for BSr
  mutate(BSr = replace_na(BSr, 0),
         BS1c = BS1-BSr,
         BS2c = BS2-BSr) %>%
  select(-c(BS1, BS2, BSr)) %>%
  # compute Total_load
  mutate(BS = round((BS1c+BS2c)/2, 0),
         WS = round((WS1+WS2)/2, 0),
         Total_load = BS + WS)
```


Read in home range/core use sizes and contours for mapping

```{r eval = F}
hr.size <- read.csv("ProcessedData/Full_HRs.csv")

AQ95 <- st_read("ProcessedData/aq2021.mkde95.shp") 

AQ50 <- st_read("ProcessedData/aq2021.mkde50.shp")

IV95 <- st_read("ProcessedData/iv2021.mkde95.shp")

IV50 <- st_read("ProcessedData/iv2021.mkde50.shp")

# Determine centroids of home ranges for mapping infection
AQcent <- st_centroid(AQ95)
IVcent <- st_centroid(IV95)
```


Read in behavioral observation annotations.

```{r eval = F}
bhav <- read.csv("Data/behave2021_updated.csv")

# Calculate observation times
follow.start <- bhav %>%
  filter(Behavior == "START/STOP") %>%
  filter(Status == "START") %>%
  rename(Start = "Time") %>%
  select(ID, Start)
n_distinct(follow.start) #86

follow.stop <- bhav %>%
  filter(Behavior == "START/STOP") %>%
  filter(Status == "STOP") %>%
  rename(Stop = "Time") %>%
  select(ID, Stop)
n_distinct(follow.stop) #86

follow.time <- left_join(follow.stop, follow.start) %>%
  mutate(Follow.Time = (Stop - Start)/60) %>%
  select(ID, Follow.Time) %>%
  separate(ID, c("Site", "Species", "Phase", "Date", "EndTime"), sep = "_")


# Format behavioral data - create time stamps for each behavior

# Start by creating a new data frame with the start times (time on watch in video) for each video observation
starts <- bhav %>%
  filter(Behavior == "Watch Time") %>%
  select(ID, Time, Modifier.1) %>%
  rename(WatchTime = Time, 
         Watch = Modifier.1)

starts$Watch <- as.POSIXct(starts$Watch, format="%H%M%S")
starts$Watch <- format(starts$Watch, "%H:%M:%S")

library(chron)

beh.fin <- plyr::join(bhav, starts, by = "ID") %>%
  separate(ID, c("Site", "Species", "Phase", "Date", "EndTime"), sep = "_", remove = F) %>%
  select(-Media.file.path, -Total.length, -FPS, -Subject, -Behavioral.category, -Comment)

beh.fin$Time <- times(beh.fin$Time / (24 * 60 * 60))
beh.fin$WatchTime <- times(beh.fin$WatchTime / (24 * 60 * 60))

beh.fin$ActualTime <- beh.fin$Watch + (beh.fin$Time - beh.fin$WatchTime)
```


Next, combine the date and actual time columns and make it POSIXct

```{r eval = F}
beh.fin$Date <- as.Date(beh.fin$Date)

beh.fin <- beh.fin %>% unite("time", c("Date", "ActualTime"), sep = " ", remove = F)

beh.fin$time <- as.POSIXct(strptime(as.character(beh.fin$time), "%Y-%m-%d %H:%M:%S"))

#Convert the actual times to UTC by adding 4 hours (EST is UTC-4 in spring/summer)
beh.fin$time <- beh.fin$time + lubridate::hours(4)

behavior <- beh.fin %>%
  select(-Site, -Species, -Phase, -Date, -EndTime, -Watch, -WatchTime)
```


Compute bite rates and get cleaning time

```{r eval = F}
bites <- behavior %>%
  filter(Behavior == "Bite" & Modifier.1 != "Feces") %>%
  group_by(ID) %>%
  summarise(N_bites = n()) %>%
  ungroup() %>%
  separate(ID, c("Site", "Species", "Phase", "Date", "EndTime"), sep = "_")

conflicts_prefer(dplyr::arrange)
conflicts_prefer(dplyr::lag)

cleaning <- behavior %>%
  filter(Behavior == "Cleaning") %>%
  arrange(ID, time) %>%
  mutate(Duration = time - lag(time)) %>%
  filter(Status == "STOP") %>%
  group_by(ID) %>%
  summarise(N_clean = n(),
            Dur_clean = as.numeric(sum(Duration))) %>%
  ungroup() %>%
  separate(ID, c("Site", "Species", "Phase", "Date", "EndTime"), sep = "_")

interact <- behavior %>%
  filter(Behavior == "Parrotfish") %>%
  arrange(ID, time) %>%
  mutate(Duration = time - lag(time)) %>%
  filter(Status == "STOP") %>%
  group_by(ID) %>%
  summarise(N_int = n(), 
            Dur_int = as.numeric(sum(Duration))) %>%
  ungroup() %>%
  separate(ID, c("Site", "Species", "Phase", "Date", "EndTime"), sep = "_")

interact2 <- behavior %>%
  filter(Behavior == "Parrotfish" & Modifier.1 == "Conspecific" & Modifier.3 == "TP") %>%
  arrange(ID, time) %>%
  mutate(Duration = time - lag(time)) %>%
  filter(Status == "STOP") %>%
  group_by(ID) %>%
  summarise(N_Cint = n(), 
            Dur_Cint = as.numeric(sum(Duration))) %>%
  ungroup() %>%
  separate(ID, c("Site", "Species", "Phase", "Date", "EndTime"), sep = "_")
```


Merge behavioral and spatial data with parasite loads

```{r eval = F}
centroids <- rbind(AQcent, IVcent) %>% select(-ID)

final.parasites <- centroids %>%
  left_join(bites) %>%
  left_join(cleaning) %>%
  left_join(interact) %>%
  left_join(interact2) %>%
  left_join(parasites) %>%
  left_join(follow.time) %>%
  filter(!is.na(Total_load)) %>%
  mutate(N_clean = ifelse(is.na(N_clean), 0, N_clean),
         Dur_clean = ifelse(is.na(Dur_clean), 0, Dur_clean),
         N_Cint = ifelse(is.na(N_Cint), 0, N_Cint),
         Dur_Cint = ifelse(is.na(Dur_Cint), 0, Dur_Cint),
         Prob_Cint = ifelse(N_Cint == 0, "0", "1"))

st_write(final.parasites, "ProcessedData/final.parasites.gpkg", driver = "GPKG", append = F) # Save as a shapefile
```


## Read in full data set

```{r}
final.parasites <- st_read("ProcessedData/final.parasites.gpkg") %>%
  mutate(logTL = log(Total_load + 1))

sp.counts <- final.parasites %>%
  group_by(Species) %>%
  summarise(N = n())
```


First, a correlation analysis to determine how close observers were in their estimates of parasite load

```{r}
# Correlations of black and white spot counts

#Sc taeniopterus
parasites.sc <- final.parasites %>% filter(Species == "Sctaeniopterus") %>%
  mutate(TL1 = WS1 + BS1c,
         TL2 = WS2 + BS2c)

cor.test(parasites.sc$BS1c, parasites.sc$BS2c,
  method = "pearson")
#r = 0.71 p < 0.001

cor.test(parasites.sc$WS1, parasites.sc$WS2,
  method = "pearson") 
#r = 0.99 p < 0.001

corr.sc.p <- ggplot(final.parasites %>% filter(Species == "Sctaeniopterus")) +
  geom_abline(slope = 1, intercept = 0, 
              lty = "dashed", color = "darkred", linewidth = 1) + # 1:1 Reference line
  geom_smooth(aes(x = WS1, y = WS2), color = "grey45", fill = "grey45",
              linewidth = 0.75, method = "lm", se = F) +
  geom_smooth(aes(x = BS1c, y = BS2c), color = "black", fill = "black",
              linewidth = 0.75, method = "lm", se = F) +
  geom_point(aes(x = WS1, y = WS2), color = "grey45", size = 0.75) +
  geom_point(aes(x = BS1c, y = BS2c), shape = 17, color = "black", size = 0.75) +
  coord_equal() + # Ensures axes have the same scale
  labs(x = "Reviewer 1 Count", y = "Reviewer 2 Count") + 
  theme_classic() +
  annotate("text", x = 0, y = 80, label = "BS r = 0.71, p < 0.001", color = "black", hjust = 0) +
  annotate("text", x = 0, y = 84, label = "WS r = 0.99, p < 0.001", color = "grey", hjust = 0)
corr.sc.p

ggsave("Figures/Parasites/obs_corr_sc_infect.png", plot = corr.sc.p,
       width = 3.25, height = 3.25, dpi = 300)

#Sp aurofrenatum

parasites.sp <- final.parasites %>% filter(Species == "Spaurofrenatum") %>%
  mutate(TL1 = WS1 + BS1c,
         TL2 = WS2 + BS2c)

cor.test(parasites.sp$BS1c, parasites.sp$BS2c,
  method = "pearson")
#r = 0.97 p < 0.001

cor.test(parasites.sp$WS1, parasites.sp$WS2,
  method = "pearson") 
#r = 0.98 p < 0.001

corr.sp.p <- ggplot(final.parasites %>% filter(Species == "Spaurofrenatum")) +
  geom_abline(slope = 1, intercept = 0, 
              lty = "dashed", color = "darkred", linewidth = 1) + # 1:1 Reference line
  geom_smooth(aes(x = WS1, y = WS2), color = "grey45", fill = "grey45",
              linewidth = 0.75, method = "lm", se = F) +
  geom_smooth(aes(x = BS1c, y = BS2c), color = "black", fill = "black",
              linewidth = 0.75, method = "lm", se = F) +
  geom_point(aes(x = WS1, y = WS2), color = "grey45", size = 0.75) +
  geom_point(aes(x = BS1c, y = BS2c), shape = 17, color = "black", size = 0.75) +
  coord_equal() + # Ensures axes have the same scale
  labs(x = "Reviewer 1 Count", y = "Reviewer 2 Count") + 
  theme_classic() +
  annotate("text", x = 0, y = 40, label = "BS r = 0.97, p < 0.001", color = "black", hjust = 0) +
  annotate("text", x = 0, y = 44, label = "WS r = 0.98, p < 0.001", color = "grey45", hjust = 0)
corr.sp.p

ggsave("Figures/Parasites/obs_corr_sp_infect.png", plot = corr.sp.p,
       width = 3.25, height = 3.25, dpi = 300)


parasites.inf <- final.parasites %>%
  filter(Total_load > 0)

parasites.inf.sum1 <- parasites.inf %>%
  group_by(Species) %>%
  summarise(N = n()) %>%
  ungroup()

parasites.inf.sum2 <- parasites.inf %>%
  mutate(propBS = BS/Total_load,
         propWS = WS/Total_load) %>%
  group_by(Species) %>%
  summarise(mPropBS = mean(propBS),
            sePropBS = sd(propBS)/sqrt(n()),
            mPropWS = mean(propWS),
            sePropWS = sd(propWS)/sqrt(n()))

spxsite.parasites <- final.parasites %>%
  group_by(Species, Site) %>%
  summarise(N_fish = n(), 
            mTL = mean(Total_load),
            seTL = sd(Total_load)/sqrt(n()))

# Correlations of total counts

# Sc taeniopterus

tl.sc <- parasites.sc %>%
  select(TL1, TL2) %>%
  st_drop_geometry() %>%
  mutate(TL1_log1p = log(TL1+1), 
         TL2_log1p = log(TL2+1))

library(irr)
# check that there are no major deviations from normality (without transformation, there were)
qqnorm(tl.sc$TL1_log1p)
qqline(tl.sc$TL1_log1p)
qqnorm(tl.sc$TL2_log1p)
qqline(tl.sc$TL2_log1p)
# all good
# check that variance is similar across observer
var(tl.sc$TL1_log1p)
var(tl.sc$TL2_log1p)
# all good
# check that one is not consistently scoring hire than the other
plot(tl.sc$TL2_log1p,tl.sc$TL1_log1p)
abline(0,1)
# all good

icc(tl.sc[, c("TL1_log1p", "TL2_log1p")], type = "agreement")
#ICC = 0.925 (0.856-0.962)

cor.test(tl.sc$TL1_log1p, tl.sc$TL2_log1p,
  method = "pearson") 
#r = 0.93 p < 0.001

corr.tot.sc.p <- ggplot(tl.sc) +
  geom_abline(slope = 1, intercept = 0, 
              lty = "dashed", color = "grey35", linewidth = 1) + # 1:1 Reference line
  # geom_smooth(aes(x = TL1_log1p, y = TL2_log1p), color = "black", fill = "black",
  #             linewidth = 0.75, method = "lm", se = F) +
  geom_point(aes(x = TL1_log1p, y = TL2_log1p), shape = 16, color = "black", size = 2) +
  coord_equal() + # Ensures axes have the same scale
  scale_x_continuous(limits = c(0,4.75)) +
  scale_y_continuous(limits = c(0,4.75)) +
  labs(x = "R1: ln(BSS Count + 1)", y = "R2: ln(BSS Count + 1)") + 
  theme_classic() + 
  annotate("text", x = 0, y = 4.5, label = "ICC = 0.925 (0.856-0.962)", color = "black", hjust = 0)
corr.tot.sc.p


# Sp aurofrenatum

tl.sp <- parasites.sp %>%
  select(TL1, TL2) %>%
  st_drop_geometry() %>%
  mutate(TL1_log1p = log(TL1+1), 
         TL2_log1p = log(TL2+1))

# check that there are no major deviations from normality (without transformation, there were)
qqnorm(tl.sp$TL1_log1p)
qqline(tl.sp$TL1_log1p)
qqnorm(tl.sp$TL2_log1p)
qqline(tl.sp$TL2_log1p)
# looks okay
# check that variance is similar across observer
var(tl.sp$TL1_log1p)
var(tl.sp$TL2_log1p)
# all good
# check that one is not consistently scoring hire than the other
plot(tl.sp$TL2_log1p,tl.sp$TL1_log1p)
abline(0,1)
# all good

icc(tl.sp[, c("TL1_log1p", "TL2_log1p")], type = "agreement")
#ICC = 0.982 (0.956-0.993)

cor.test(tl.sp$TL1_log1p, tl.sp$TL2_log1p,
  method = "pearson") 
#r = 0.98 p < 0.001

corr.tot.sp.p <- ggplot(tl.sp) +
  geom_abline(slope = 1, intercept = 0, 
              lty = "dashed", color = "grey35", linewidth = 1) + # 1:1 Reference line
  # geom_smooth(aes(x = TL1, y = TL2), color = "black", fill = "black",
  #             linewidth = 0.75, method = "lm", se = T) +
  geom_point(aes(x = TL1_log1p, y = TL2_log1p), shape = 16, color = "black", size = 2) +
  coord_equal() + # Ensures axes have the same scale
  scale_x_continuous(limits = c(0,4.75)) +
  scale_y_continuous(limits = c(0,4.75)) +
  labs(x = "R1: ln(BSS Count + 1)", y = "R2: ln(BSS Count + 1)") +
  theme_classic() +
  annotate("text", x = 0, y = 4.5, label = "ICC = 0.982 (0.956-0.993)", color = "black", hjust = 0)
corr.tot.sp.p

corr.p <- ggarrange(corr.tot.sc.p, corr.tot.sp.p,
                     labels = c("a", "b"),
                     ncol = 2, nrow = 1, align = "h",
                     font.label = list(size = 12, color = "black", face = "plain", family = "Arial"))
corr.p

ggsave("Figures/Parasites/obs_corr_infect.png", plot = corr.p,
       width = 6.5, height = 3.25, dpi = 300)
```


## Let's do a more formal concordance correlation analysis

```{r eval = F}
library(iccCounts) 

# Total counts

# Sc. taeniopterus

parasites.sc.long.tot <- parasites.sc %>% 
  st_drop_geometry() %>%
  unite("id", c(Site:EndTime), sep = "_") %>%
  select(id, WS1, WS2, BS1c, BS2c) %>%
  mutate(Tot1 = WS1 + BS1c,
         Tot2 = WS2 + BS2c) %>%
  select(id, Tot1, Tot2) %>%
  gather(key = "rev", value = "count", c(Tot1:Tot2))


sc.tot.pois1a <- icc_counts(data = parasites.sc.long.tot,
                          y = "count", id = "id", met = "rev", type = "con",
                          fam = "poisson")
sc.tot.pois1b <-icc_counts(data = parasites.sc.long.tot,
                           y = "count", id = "id", met = "rev", type = "con",
                           fam = "zip")
# sc.tot.nb1a <- icc_counts(data = parasites.sc.long.tot,
#                           y = "count", id = "id", met = "rev", type = "con",
#                           fam = "nbinom1")
# sc.tot.nb1b <-icc_counts(data = parasites.sc.long.tot,
#                            y = "count", id = "id", met = "rev", type = "con",
#                            fam = "zinb1")
# sc.tot.nb2a <- icc_counts(data = parasites.sc.long.tot,
#                           y = "count", id = "id", met = "rev", type = "con",
#                           fam = "nbinom2")
# sc.tot.nb2b <-icc_counts(data = parasites.sc.long.tot,
#                            y = "count", id = "id", met = "rev", type = "con",
#                            fam = "zinb2")

# model convergence issues on all of the negative binomial models

AIC(sc.tot.pois1a$model, sc.tot.pois1b$model)

# , 
#     sc.tot.nb1a$model, sc.tot.nb1b$model, 
#     sc.tot.nb2a$model, sc.tot.nb2b$model)

# poisson model best fit anyway

summary(sc.tot.pois1a$model)
ICC(sc.tot.pois1a)

set.seed(100)
sc.tot.pois1a.gof <- GOF_check(sc.tot.pois1a) # this is slow FYI and can fail (up seed?)

plot(sc.tot.pois1a.gof, type = "envelope") # some points out of envelope, mostly at lower end
plot(sc.tot.pois1a.gof, type = "dispersion") 
DispersionTest(sc.tot.pois1a.gof) # good
plot(sc.tot.pois1a.gof, type = "zeros") 
ZeroTest(sc.tot.pois1a.gof) # good


# Sp aurofrenatum

parasites.sp.long.tot <- parasites.sp %>% 
  unite("id", c(Site:EndTime), sep = "_") %>%
  select(id, WS1, WS2, BS1c, BS2c) %>%
  mutate(Tot1 = WS1 + BS1c,
         Tot2 = WS2 + BS2c) %>%
  select(id, Tot1, Tot2) %>%
  gather(key = "rev", value = "count", c(Tot1:Tot2))


sp.tot.pois1a <- icc_counts(data = parasites.sp.long.tot,
                          y = "count", id = "id", met = "rev", type = "con",
                          fam = "poisson")
sp.tot.pois1b <-icc_counts(data = parasites.sp.long.tot,
                           y = "count", id = "id", met = "rev", type = "con",
                           fam = "zip")
sp.tot.nb1a <- icc_counts(data = parasites.sp.long.tot,
                          y = "count", id = "id", met = "rev", type = "con",
                          fam = "nbinom1")
sp.tot.nb1b <-icc_counts(data = parasites.sp.long.tot,
                           y = "count", id = "id", met = "rev", type = "con",
                           fam = "zinb1")
sp.tot.nb2a <- icc_counts(data = parasites.sp.long.tot,
                          y = "count", id = "id", met = "rev", type = "con",
                          fam = "nbinom2")
sp.tot.nb2b <-icc_counts(data = parasites.sp.long.tot,
                           y = "count", id = "id", met = "rev", type = "con",
                           fam = "zinb2")

# model convergence issues on all of the negative binomial models

AIC(sp.tot.pois1a$model, sp.tot.pois1b$model)
    
    # , 
    # sp.tot.nb1a$model, sp.tot.nb1b$model, 
    # sp.tot.nb2a$model, sp.tot.nb2b$model)

# poisson model best fit anyway

summary(sp.tot.pois1a$model)
ICC(sp.tot.pois1a)

set.seed(100)
sp.tot.pois1a.gof <- GOF_check(sp.tot.pois1a) # this is slow FYI and can fail (up seed?)

plot(sp.tot.pois1a.gof, type = "envelope") # points out of envelope
plot(sp.tot.pois1a.gof, type = "dispersion") 
DispersionTest(sp.tot.pois1a.gof) # good
plot(sp.tot.pois1a.gof, type = "zeros") 
ZeroTest(sp.tot.pois1a.gof) # good


# Merge both species into one due to lack of sample size...

parasites.long.tot <- rbind(parasites.sc.long.tot, parasites.sp.long.tot)


tot.pois1a <- icc_counts(data = parasites.long.tot,
                          y = "count", id = "id", met = "rev", type = "con",
                          fam = "poisson")
tot.pois1b <-icc_counts(data = parasites.long.tot,
                           y = "count", id = "id", met = "rev", type = "con",
                           fam = "zip")
tot.nb1a <- icc_counts(data = parasites.long.tot,
                          y = "count", id = "id", met = "rev", type = "con",
                          fam = "nbinom1")
tot.nb1b <-icc_counts(data = parasites.long.tot,
                           y = "count", id = "id", met = "rev", type = "con",
                           fam = "zinb1")
tot.nb2a <- icc_counts(data = parasites.long.tot,
                          y = "count", id = "id", met = "rev", type = "con",
                          fam = "nbinom2")
tot.nb2b <-icc_counts(data = parasites.long.tot,
                           y = "count", id = "id", met = "rev", type = "con",
                           fam = "zinb2")

# model convergence issues on all of the negative binomial models

AIC(tot.pois1a$model, tot.pois1b$model)

# poisson model best fit anyway

summary(tot.pois1a$model)
ICC(tot.pois1a)

set.seed(100)
tot.pois1a.gof <- GOF_check(tot.pois1a) # this is slow FYI and can fail (up seed?)

plot(tot.pois1a.gof, type = "envelope") # some points out of envelope
plot(tot.pois1a.gof, type = "dispersion") 
DispersionTest(tot.pois1a.gof) # good
plot(tot.pois1a.gof, type = "zeros") 
ZeroTest(tot.pois1a.gof) # good


# Now we could split to check for black spots and white spots...

parasites.sc.long.ws <- parasites.sc %>% 
  unite("id", c(Site:EndTime), sep = "_") %>%
  select(id, WS1, WS2) %>%
  gather(key = "rev", value = "count", c(WS1:WS2))

parasites.sc.long.bs <- parasites.sc %>% 
  unite("id", c(Site:EndTime), sep = "_") %>%
  select(id, BS1c, BS2c) %>%
  gather(key = "rev", value = "count", c(BS1c:BS2c))
```


## Map the infections

```{r eval = F}
AQ_SPA_SCT_HR <- ggplot() +
  geom_sf(data = final.parasites %>% filter(Site == "AQ"), 
          aes(color = Species, size = Total_load), linewidth = 0.5, alpha = 0.2) +
  coord_sf(datum = st_crs(32619)) +
  theme_classic() +
  scale_x_continuous("Easting (m)", limits = c(577630, 577720), breaks = c(577635, 577675, 577715)) +
  scale_y_continuous("Northing (m)", limits = c(1337440, 1337560), 
                     breaks = c(1337420, 1337460, 1337500, 1337540, 1337580)) + 
  theme(axis.title = element_text(size = 12, color = "black"),
        axis.text = element_text(size = 10, color = "black"),
        panel.border = element_rect(color = "black", fill = NA, linewidth = 2)) +
  labs(color = "Species", size = "Load") +
  scale_color_manual(labels = c("Princess", "Redband"), values = c("navy", "darkred")) +
  annotate("text", x = 577705, y = 1337555, label = "Aquarius") +
  guides(color = guide_legend(order = 1))
AQ_SPA_SCT_HR

#Save figure
ggsave("Figures/Parasites/AQ_parasiteloads.png", plot = AQ_SPA_SCT_HR,
       width = 4, height = 4, dpi = 300)

IV_SPA_SCT_HR <- ggplot() +
  geom_sf(data = final.parasites %>% filter(Site == "IV"), 
          aes(color = Species, size = Total_load), linewidth = 0.5, alpha = 0.2) +
  coord_sf(datum = st_crs(32619)) +
  theme_classic() +
  scale_x_continuous("Easting (m)", limits = c(578130, 578195), breaks = c(578140, 578165, 578190)) +
  scale_y_continuous("Northing (m)", limits = c(1335260, 1335345), 
                     breaks = c(1335265, 1335290, 1335315, 1335340)) +
  theme(axis.title = element_text(size = 12, color = "black"),
        axis.text = element_text(size = 10, color = "black"),
        panel.border = element_rect(color = "black", fill = NA, linewidth = 2)) +
  labs(color = "Species", size = "Load") +
  scale_color_manual(labels = c("Princess", "Redband"), values = c("navy", "darkred"))  +
  annotate("text", x = 578185, y = 1335340, label = "Invisibles") +
  guides(color = guide_legend(order = 1))
IV_SPA_SCT_HR

ggsave("Figures/Parasites/IV_parasiteloads.png", plot = IV_SPA_SCT_HR,
       width = 4, height = 4, dpi = 300)
```


Bites, territorial interactions, and cleaning as a function of infection

```{r}
# Bites
bite.para.m1 <- glmmTMB(data = final.parasites, 
                       N_bites ~ Site*Species + Site*logTL + Species*logTL +
                         offset(log(Follow.Time)), family = nbinom2())

test.bite.para <- simulateResiduals(fittedModel = bite.para.m1, n = 250, plot = T)
summary(bite.para.m1)
options(contrasts = c("contr.sum", "contr.poly"))
Anova(bite.para.m1, type = 3)
# Interaction terms involving total load are not significant, so remove

bite.para.m2 <- glmmTMB(data = final.parasites, 
                       N_bites ~ Site*Species + logTL +
                         offset(log(Follow.Time)), family = nbinom2())

test.bite.para <- simulateResiduals(fittedModel = bite.para.m2, n = 250, plot = T)
summary(bite.para.m2)
options(contrasts = c("contr.sum", "contr.poly"))
Anova(bite.para.m2, type = 3)
fixef(bite.para.m2)


# Visualize effect of BSS counts

# 1. Create data frame

new.bites <- final.parasites %>%
  group_by(Species) %>%
  summarise(logTL = list(seq(min(logTL, na.rm = TRUE),
                             max(logTL, na.rm = TRUE),
                             length.out = 100)),
            .groups = "drop") %>%
  unnest(logTL) %>%
  mutate(Site = "AQ",
         Follow.Time = median(final.parasites$Follow.Time))

# 2. Predict from the model

preds <- predict(
  bite.para.m2,
  newdata = new.bites,
  type = "link",
  se.fit = TRUE)

new.bites$fit <- exp(preds$fit)
new.bites$lower <- exp(preds$fit - 1.96 * preds$se.fit)
new.bites$upper <- exp(preds$fit + 1.96 * preds$se.fit)
new.bites$eta <- preds$fit
new.bites$se <- preds$se.fit

# 3. Plot
bites.p <- ggplot() +
  geom_point(data = final.parasites, aes(x = logTL, y = N_bites, color = Species), 
             size = 0.5, alpha = 0.5) +
  geom_line(data = new.bites, aes(x = logTL, y = fit, color = Species), 
            linewidth = 1) +
  geom_ribbon(data = new.bites, aes(x = logTL, ymin = lower, ymax = upper, fill = Species), 
              alpha = 0.2, color = NA) +
  labs(x = "ln(BSS Lessions + 1)", y = expression(paste("Bites 20-min"^-1))) +
  theme_classic() +
  scale_color_manual(values = c(sct.color, spa.color), 
                     label = c(expression(italic("Sc. taeniopterus")), 
                               expression(italic("Sp. aurofrenatum")))) +
  scale_fill_manual(values = c(sct.color, spa.color)) +
  guides(color = "none", fill = "none") +
  theme(legend.text = element_text(hjust = 0)) # Left-justify legend labels
bites.p

# ggsave("Figures/Parasites/bites.png", plot = bites.p,
#        width = 5.5, height = 3, dpi = 300)


# Visualize species differences

# 1. Create data frame

new.bites2 <- final.parasites %>%
  group_by(Species) %>%
  summarise(logTL = median(logTL, na.rm = TRUE),
            .groups = "drop") %>%
  mutate(Site = "AQ",
         Follow.Time = median(final.parasites$Follow.Time))

# 2. Predict from the model

preds2 <- predict(
  bite.para.m2,
  newdata = new.bites2,
  type = "link",
  se.fit = TRUE)

new.bites2$fit <- exp(preds2$fit)
new.bites2$lower <- exp(preds2$fit - 1.96 * preds2$se.fit)
new.bites2$upper <- exp(preds2$fit + 1.96 * preds2$se.fit)

# 3. Plot
bites.p2 <- ggplot() +
  geom_jitter(data = final.parasites, aes(x = Species, y = N_bites, color = Species), 
             width = 0.1, size = 0.5, alpha = 0.5) +
  geom_point(data = new.bites2, aes(x = Species, y = fit, color = Species), 
             size = 2) +
  geom_errorbar(data = new.bites2, aes(x = Species, ymin = lower, ymax = upper, color = Species), 
                width = 0, linewidth = 1) +
  labs(x = "Species", y = expression(paste("Bites 20-min"^-1))) +
  theme_classic() +
  scale_x_discrete(labels = c(expression(italic("Sc. taeniopterus")), 
                               expression(italic("Sp. aurofrenatum")))) +
  scale_color_manual(values = c(sct.color, spa.color)) +
  guides(color = "none",
         fill = "none") +
  theme(legend.text = element_text(hjust = 0)) # Left-justify legend labels
bites.p2

# ggsave("Figures/Parasites/bites2.png", plot = bites.p2,
#        width = 4, height = 3, dpi = 300)


bites.m.p <- ggarrange(bites.p, bites.p2, ncol = 2, nrow = 1, labels = c("a", "b"), 
                       font.label = list(size = 10, color = "black"))
bites.m.p

ggsave("Figures/Parasites/bites.results.png", plot = bites.m.p,
       width = 6.5, height = 3, dpi = 300)



# Parrotfish interactions

ic.para.m1 <- glmmTMB(data = final.parasites, 
                      N_Cint ~ Site*Species + Site*logTL + Species*logTL + 
                        offset(log(Follow.Time)), family = nbinom2())

test.ic.para <- simulateResiduals(fittedModel = ic.para.m1, n = 250, plot = T)
testZeroInflation(test.ic.para)
summary(ic.para.m1)
options(contrasts = c("contr.sum", "contr.poly"))
Anova(ic.para.m1, type = 3)

# No significant interaction with total load for either of the categorical main effects, so remove

ic.para.m2 <- glmmTMB(data = final.parasites, 
                      N_Cint ~ Site*Species + logTL + 
                        offset(log(Follow.Time)), family = nbinom2())

test.ic.para2 <- simulateResiduals(fittedModel = ic.para.m2, n = 250, plot = T)
testZeroInflation(test.ic.para2)
summary(ic.para.m2)
options(contrasts = c("contr.sum", "contr.poly"))
Anova(ic.para.m2, type = 3)
fixef(ic.para.m2)

# Visualize total BSS counts on agonisms

new.ints <- final.parasites %>%
  group_by(Species) %>%
  summarise(min_logTL = min(logTL, na.rm = TRUE),
            max_logTL = max(logTL, na.rm = TRUE),
            .groups = "drop") %>%
  rowwise() %>%
  do(data.frame(Species = .$Species,
                logTL = seq(.$min_logTL, .$max_logTL, length.out = 100))) %>%
  ungroup() %>%
  mutate(Site = "AQ",
         Follow.Time = median(final.parasites$Follow.Time))

preds.int <- predict(
  ic.para.m2,
  newdata = new.ints,
  type = "link",
  se.fit = TRUE
)

new.ints$fit <- exp(preds.int$fit)
new.ints$lower <- exp(preds.int$fit - 1.96 * preds.int$se.fit)
new.ints$upper <- exp(preds.int$fit + 1.96 * preds.int$se.fit)

ints.p <- ggplot() +
  geom_point(data = final.parasites, aes(x = logTL, y = N_Cint, color = Species), 
             size = 0.5, alpha = 0.5) +
  geom_line(data = new.ints, aes(x = logTL, y = fit, color = Species), 
            linewidth = 1) +
  geom_ribbon(data = new.ints, aes(x = logTL, ymin = lower, ymax = upper, fill = Species), 
              alpha = 0.2, color = NA) +
  labs(x = "ln(BSS Lesions + 1)", y = expression(paste("Agonisms 20-min"^-1))) +
  theme_classic() +
  scale_color_manual(values = c(sct.color, spa.color), 
                     label = c(expression(italic("Sc. taeniopterus")), 
                               expression(italic("Sp. aurofrenatum")))) +
  scale_fill_manual(values = c(sct.color, spa.color)) +
  guides(color = "none",
         fill = "none") +
  theme(legend.text = element_text(hjust = 0)) # Left-justify legend labels
ints.p

ggsave("Figures/Parasites/int_counts.png", plot = ints.p,
       width = 6.5, height = 3, dpi = 300)

# Visualize site by species effect on agonisms

# new.ints2 <- expand.grid(
#   logTL = median(final.parasites$logTL), # set site as constant
#   Species = unique(final.parasites$Species),
#   Site = unique(final.parasites$Site),
#   Follow.Time = median(final.parasites$Follow.Time)) # constant offset

new.ints2 <- final.parasites %>%
  group_by(Species) %>%
  summarise(logTL = median(logTL, na.rm = TRUE),
            .groups = "drop") %>%
  crossing(Site = unique(final.parasites$Site)) %>%
  mutate(Follow.Time = median(final.parasites$Follow.Time))

preds.int2 <- predict(
  ic.para.m2,
  newdata = new.ints2,
  type = "link",
  se.fit = TRUE
)

new.ints2$fit <- exp(preds.int2$fit)
new.ints2$lower <- exp(preds.int2$fit - 1.96 * preds.int2$se.fit)
new.ints2$upper <- exp(preds.int2$fit + 1.96 * preds.int2$se.fit)

ints.p2 <- ggplot() +
  geom_point(data = final.parasites, aes(x = Site, y = N_Cint, color = Species), 
             position = position_jitterdodge(jitter.width = 0.1, dodge.width = 0.3), 
             size = 0.5, alpha = 0.5) +
  geom_point(data = new.ints2, aes(x = Site, y = fit, color = Species),
             position = position_dodge(width = 0.3), size = 2) +
  geom_errorbar(data = new.ints2, aes(x = Site, ymin = lower, ymax = upper, color = Species),
                position = position_dodge(width = 0.3), width = 0, linewidth = 1) +
  labs(x = "Site", y = expression(paste("Agonisms 20-min"^-1))) +
  theme_classic() +
  scale_color_manual(values = c(sct.color, spa.color), 
                     label = c(expression(italic("Sc. taeniopterus")), 
                               expression(italic("Sp. aurofrenatum")))) +
  scale_x_discrete(labels = c("Aquarius", "Invisibles")) +
  scale_fill_manual(values = c(sct.color, spa.color)) +
  guides(color = "none", 
         fill = "none") +
  theme(legend.text = element_text(hjust = 0)) # Left-justify legend labels
ints.p2

ggsave("Figures/Parasites/int_counts2.png", plot = ints.p2,
       width = 4, height = 3, dpi = 300)


ints.m.p <- ggarrange(ints.p, ints.p2, ncol = 2, nrow = 1, labels = c("a", "b"), 
                       font.label = list(size = 10, color = "black"))
ints.m.p

ggsave("Figures/Parasites/ints.results.png", plot = ints.m.p,
       width = 6.5, height = 3, dpi = 300)



#Home range area

hr.para.m1 <- glmmTMB(data = final.parasites, area ~ Site*Species + Site*logTL + Species*logTL + 
                        offset(log(Follow.Time)), family = "gaussian")
test.hr.para <- simulateResiduals(fittedModel = hr.para.m1, n = 250, plot = T)
summary(hr.para.m1)
options(contrasts = c("contr.sum", "contr.poly"))
Anova(hr.para.m1, type = 3)
fixef(hr.para.m1)


# Visualize species by load effect on foraging area

# new.hr <- expand.grid(
#   logTL = seq(min(final.parasites$logTL), max(final.parasites$logTL), length.out = 100),
#   Species = unique(final.parasites$Species),
#   Site = "AQ", #set site as constant
#   Follow.Time = median(final.parasites$Follow.Time)) #constant offset

new.hr <- final.parasites %>%
  group_by(Species) %>%
  summarise(logTL = list(seq(min(logTL, na.rm = TRUE),
                             max(logTL, na.rm = TRUE),
                             length.out = 100)),
            .groups = "drop") %>%
  unnest(logTL) %>%
  mutate(Site = "AQ",
         Follow.Time = median(final.parasites$Follow.Time))

preds.hr <- predict(
  hr.para.m1,
  newdata = new.hr,
  type = "response", # Gaussian model
  se.fit = TRUE
)

new.hr$fit <- preds.hr$fit
new.hr$lower <- preds.hr$fit - 1.96 * preds.hr$se.fit
new.hr$upper <- preds.hr$fit + 1.96 * preds.hr$se.fit
new.hr$se <- preds.hr$se.fit

hr.p <- ggplot() +
  geom_point(data = final.parasites, aes(x = logTL, y = area, color = Species), 
             size = 0.5, alpha = 0.5) +
  geom_line(data = new.hr, aes(x = logTL, y = fit, color = Species), 
            linewidth = 1) +
  geom_ribbon(data = new.hr, aes(x = logTL, ymin = lower, ymax = upper, fill = Species), 
              alpha = 0.2, color = NA) +
  labs(x = "ln(BSS Lesions + 1)", y = expression(paste("Foraging Area (m"^2~")"))) +
  theme_classic() +
  scale_color_manual(values = c(sct.color, spa.color), 
                     label = c(expression(italic("Sc. taeniopterus")), 
                               expression(italic("Sp. aurofrenatum")))) +
  scale_fill_manual(values = c(sct.color, spa.color)) +
  guides(color = "none",
         fill = "none") +
  theme(legend.text = element_text(hjust = 0)) # Left-justify legend labels
hr.p

ggsave("Figures/Parasites/homerange.png", plot = hr.p,
       width = 6.5, height = 3, dpi = 300)


# Visualize site by species differences in foraging area

# new.hr2 <- expand.grid(
#   logTL = median(final.parasites$logTL), # set site as constant
#   Species = unique(final.parasites$Species),
#   Site = unique(final.parasites$Site),
#   Follow.Time = median(final.parasites$Follow.Time)) # constant offset

new.hr2 <- final.parasites %>%
  group_by(Species) %>%
  summarise(logTL = median(logTL, na.rm = TRUE),
            .groups = "drop") %>%
  crossing(Site = unique(final.parasites$Site)) %>%
  mutate(Follow.Time = median(final.parasites$Follow.Time))

preds.hr2 <- predict(
  hr.para.m1,
  newdata = new.hr2,
  type = "response", # Gaussian model
  se.fit = TRUE
)

new.hr2$fit <- preds.hr2$fit
new.hr2$lower <- preds.hr2$fit - 1.96 * preds.hr2$se.fit
new.hr2$upper <- preds.hr2$fit + 1.96 * preds.hr2$se.fit

hr.p2 <- ggplot() +
  geom_point(data = final.parasites, aes(x = Site, y = area, color = Species), 
             position = position_jitterdodge(jitter.width = 0.1, dodge.width = 0.3), 
             size = 0.5, alpha = 0.5) +
  geom_point(data = new.hr2, aes(x = Site, y = fit, color = Species),
             position = position_dodge(width = 0.3), size = 2) +
  geom_errorbar(data = new.hr2, aes(x = Site, ymin = lower, ymax = upper, color = Species),
                position = position_dodge(width = 0.3), width = 0, linewidth = 1) +
  labs(x = "Site", y = expression(paste("Foraging Area (m"^2~")"))) +
  theme_classic() +
  scale_color_manual(values = c(sct.color, spa.color), 
                     label = c(expression(italic("Sc. taeniopterus")), 
                               expression(italic("Sp. aurofrenatum")))) +
  scale_x_discrete(labels = c("Aquarius", "Invisibles")) +
  scale_fill_manual(values = c(sct.color, spa.color)) +
  guides(color = "none", 
         fill = "none") +
  theme(legend.text = element_text(hjust = 0)) # Left-justify legend labels
hr.p2

ggsave("Figures/Parasites/homerange2.png", plot = hr.p2,
       width = 4, height = 3, dpi = 300)


hr.m.p <- ggarrange(hr.p, hr.p2, ncol = 2, nrow = 1, labels = c("a", "b"), 
                       font.label = list(size = 10, color = "black"))
hr.m.p

ggsave("Figures/Parasites/hr.results.png", plot = hr.m.p,
       width = 6.5, height = 3, dpi = 300)
```





## Investigating relationship between BSS infection and per area grazing CaCO3 removed

```{r eval = F}
set.seed(123)

bites.grps <- final.parasites %>%
  group_by(Species) %>%
  summarise(
    logTL = list(c(
      min(logTL, na.rm = TRUE),
      median(logTL, na.rm = TRUE),
      max(logTL, na.rm = TRUE)
    )),
    .groups = "drop"
  ) %>%
  unnest(logTL) %>%
  mutate(
    Site = "AQ",
    Follow.Time = median(final.parasites$Follow.Time, na.rm = TRUE)
  ) 

preds.sim <- predict(
  bite.para.m2,
  newdata = bites.grps,
  type = "link",
  se.fit = TRUE
)

bites.grps$eta <- preds.sim$fit
bites.grps$se <- preds.sim$se.fit

bites.grps.sc <- bites.grps %>% filter(Species == "Sctaeniopterus")
bites.grps.sp <- bites.grps %>% filter(Species == "Spaurofrenatum")


library(purrr)

nsim <- 250

sim.sc.bites <- bites.grps.sc %>%
  mutate(sim_eta = map2(eta, se, ~ rnorm(nsim, .x, .y))) %>%
  unnest(sim_eta) %>%
  mutate(bites_20min = exp(sim_eta)) %>%
  select(Species, logTL, bites_20min)

sim.sp.bites <- bites.grps.sp %>%
  mutate(sim_eta = map2(eta, se, ~ rnorm(nsim, .x, .y))) %>%
  unnest(sim_eta) %>%
  mutate(bites_20min = exp(sim_eta)) %>%
  select(Species, logTL, bites_20min)

sim.bites <- rbind(sim.sc.bites, sim.sp.bites) %>%
  rownames_to_column()


erosion.df <- lengths %>%
  select(Species, mFL) %>%
         # Adam et al. 2018
  mutate(prop_bite_scars = ifelse(Species == "Sctaeniopterus", 0.22, 0.06),
         # Average from ReefBudget methodology June 2024 (could use the mean and sd from the July 2024)
         substrate_dens = 1.72,
         # Bellwood et al. 1995
         prop_day_feed = ifelse(Species == "Sctaeniopterus", 0.877, 0.833),
         # Bruggemann et al. 1996 using Sc. vetula equations for both
         vol_slope_draw = rnorm(1, 0.193, 0.020),
         area_slope_draw = rnorm(1, 4.013, 0.241),
         cm3_per_bite = vol_slope_draw*(10^-6)*(mFL^3),
         cm2_per_bite = area_slope_draw*(10^-4)*(mFL^2))

sim.bites.eq <- sim.bites %>%
  left_join(erosion.df) %>%
  mutate(bites_min = bites_20min/20,
         bites_wscar_min = bites_min*prop_bite_scars,
         cm2_day = bites_wscar_min*cm2_per_bite*60*12*prop_day_feed,
         cm3_day = bites_wscar_min*cm3_per_bite*60*12*prop_day_feed,
         kg_day = (cm3_day*substrate_dens)/1000,
         m2_year = (cm2_day*365)/10000,
         kg_year = kg_day*365,
         severity = ifelse(logTL < 1, "Low", "High"))

sim.bites.eq.sum <- sim.bites.eq %>%
  group_by(Species, logTL) %>%
  summarise(N = n(),
            mArea = mean(m2_year),
            seArea = sd(m2_year)/sqrt(N),
            mMass = mean(kg_year),
            seMass = sd(kg_year)/sqrt(N))

# Surface area grazed per year

ggplot(data = sim.bites.eq %>% filter(Species == "Sctaeniopterus"), 
       aes(x = logTL, y = m2_year, color = Species)) +
  stat_summary(fun = mean, geom = "point", size = 2, 
    position = position_dodge(width = 0.3)) +
  stat_summary(fun.data = mean_cl_normal,  # mean ± 1.96*SE (approx CI)
    geom = "errorbar", width = 0, linewidth = 0.5,
    position = position_dodge(width = 0.3), color = "black") +
  labs(x = "BSS Severity", y = expression("Area Cleared (m"^2~" yr"^-1~")")) +
  theme_classic() +
  # facet_wrap(~Species, scales = "free", 
  #            labeller = labeller(Species = c(Sctaeniopterus = "Sc. taeniopterus",
  #                                            Spaurofrenatum = "Sp. aurofrenatum"))) +
  scale_color_manual(values = c(sct.color, spa.color)) +
  guides(color = "none") +
  theme(strip.background = element_blank())


ggplot(data = sim.bites.eq %>% filter(Species == "Sctaeniopterus"), 
       aes(x = logTL, y = kg_year, color = Species)) +
  stat_summary(fun = mean, geom = "point", size = 2, 
    position = position_dodge(width = 0.3)) +
  stat_summary(fun.data = mean_cl_normal,  # mean ± 1.96*SE (approx CI)
    geom = "errorbar", width = 0, linewidth = 0.5,
    position = position_dodge(width = 0.3), color = "black") +
  labs(x = "BSS Severity", y = expression("Erosion Rate (kg CaCO"[3]~"yr"^-1~")")) +
  theme_classic() +
  # facet_wrap(~Species, scales = "free", 
  #            labeller = labeller(Species = c(Sctaeniopterus = "Sc. taeniopterus",
  #                                            Spaurofrenatum = "Sp. aurofrenatum"))) +
  scale_color_manual(values = c(sct.color, spa.color)) +
  guides(color = "none") +
  theme(strip.background = element_blank())

# sim.sc.hr <- hr.grps.sc %>%
#   mutate(area = map2(fit, se, ~ rnorm(nsim, mean = .x, sd = .y))) %>%
#   unnest(area) %>%
#   select(Species, logTL, area) 
# 
# sim.sp.hr <- hr.grps.sp %>%
#   mutate(area = map2(fit, se, ~ rnorm(nsim, mean = .x, sd = .y))) %>%
#   unnest(area) %>%
#   select(Species, logTL, area) 
# 
# sim.hr <- rbind(sim.sc.hr, sim.sp.hr) %>%
#   rownames_to_column()
# 
# 
# sim <- sim.bites %>%
#   left_join(sim.hr) %>%
#   mutate(bites_hr = bites_20min*3,
#          forage_hr = ifelse(Species == "Sctaeniopterus", 12*0.877, 12*0.833),
#          bites_day = bites_hr * forage_hr,
#          bites_day_m2 = bites_day/area,
#          severity = ifelse(logTL < 1, "Low", "High"))

```


```{r}
set.seed(123)
nsim <- 1000

bites.grps <- final.parasites %>%
  group_by(Species) %>%
  summarise(logTL = list(c(min(logTL, na.rm = TRUE),
                           median(logTL, na.rm = TRUE),
                           max(logTL, na.rm = TRUE))),
            .groups = "drop") %>%
  unnest(logTL) %>%
  mutate(Site = "AQ",
         Follow.Time = median(final.parasites$Follow.Time, na.rm = TRUE))

preds.sim <- predict(bite.para.m2, newdata = bites.grps,
                     type = "link", se.fit = TRUE)

bites.grps$eta <- preds.sim$fit
bites.grps$se  <- preds.sim$se.fit


# Monte Carlo simulations

sim.results <- map(seq_len(nsim), function(i) {

  # Re-draw area and volume removed slopes each iteration
  area.slope <- rnorm(1, 4.013, 0.241)
  vol.slope  <- rnorm(1, 0.193, 0.020)

  bites.grps %>%
    mutate(iter = i,
           sim_eta = rnorm(n(), eta, se),   # bite rate noise per row
           bites_20min = exp(sim_eta),
           vol_slope = vol.slope,
           area_slope = area.slope)
}) %>%
  list_rbind()


# Join area grazed and erosion data with everything else and compute metrics

erosion.params <- lengths %>%
  select(Species, mFL) %>%
  mutate(prop_bite_scars = ifelse(Species == "Sctaeniopterus", 0.22,  0.06),
         substrate_dens  = 1.72,
         prop_day_feed   = ifelse(Species == "Sctaeniopterus", 0.877, 0.833))

sim.erosion <- sim.results %>%
  left_join(erosion.params, by = "Species") %>%
  mutate(cm3_per_bite = vol_slope  * (10^-6) * (mFL^3),
         cm2_per_bite = area_slope * (10^-4) * (mFL^2),
         bites_min = bites_20min / 20,
         bites_wscar_min = bites_min * prop_bite_scars,
         cm2_day  = bites_wscar_min * cm2_per_bite * 60 * 12 * prop_day_feed,
         cm3_day  = bites_wscar_min * cm3_per_bite * 60 * 12 * prop_day_feed,
         kg_day   = (cm3_day * substrate_dens) / 1000,
         m2_year  = (cm2_day * 365) / 10000,
         kg_year  = kg_day * 365,
         Total_load = round(exp(logTL)-1),
         severity = ifelse(Total_load <= 2, "Min", ifelse(Total_load >= 54, "Max", "Median"))) %>%
  mutate(severity = factor(severity, levels = c("Min", "Median", "Max")))


# area.m1 <- glmmTMB(m2_year ~ severity, family = gaussian(link = "log"), 
#                    data = sim.erosion %>% filter(Species == "Sctaeniopterus"))
# test.area <- simulateResiduals(fittedModel = area.m1, n = 250, plot = T)
# summary(area.m1)
# 
# 
# erosion.m1 <- glmmTMB(kg_year ~ severity, family = gaussian(link = "log"), 
#                    data = sim.erosion %>% filter(Species == "Sctaeniopterus"))
# test.erosion <- simulateResiduals(fittedModel = erosion.m1, n = 250, plot = T)
# summary(erosion.m1)


sct.erosion <- sim.erosion %>% filter(Species == "Sctaeniopterus")


library(rstatix)
kruskal.test(m2_year ~ severity, data = sct.erosion)
dunn_test(m2_year ~ severity, data = sct.erosion)

kruskal.test(kg_year ~ severity, data = sct.erosion)
dunn_test(kg_year ~ severity, data = sct.erosion)


# Summarise

erosion.summary <- sim.erosion %>%
  group_by(Species, logTL, Total_load, severity) %>%
  summarise(across(c(bites_20min, kg_year, m2_year),
                   list(mean = mean,
                        lo95   = ~ quantile(.x, 0.025),
                        hi95   = ~ quantile(.x, 0.975)),
                   .names = "{.col}_{.fn}"),
            .groups = "drop")

# Plot

area.grazed.p <- ggplot(data = erosion.summary %>% filter(Species == "Sctaeniopterus"), 
       aes(x = severity, y = m2_year_mean)) +
  geom_point(stat = "identity", color = sct.color, size = 2) +
  geom_errorbar(aes(x = severity, ymin = m2_year_lo95, ymax = m2_year_hi95), 
                color = sct.color, width = 0, linewidth = 0.5) +
  labs(x = "BSS Severity", y = expression("Area Cleared (m"^2~"ind"^-1~"y"^-1~")")) +
  theme_classic() +
  theme(strip.background = element_blank())
area.grazed.p

mass.removed.p <- ggplot(data = erosion.summary %>% filter(Species == "Sctaeniopterus"), 
       aes(x = severity, y = kg_year_mean)) +
  geom_point(stat = "identity", color = sct.color, size = 2) +
  geom_errorbar(aes(x = severity, ymin = kg_year_lo95, ymax = kg_year_hi95), 
                color = sct.color, width = 0, linewidth = 0.5) +
  labs(x = "BSS Severity", y = expression("Bioerosion (kg CaCO"[3]~"ind"^-1~"y"^-1~")")) +
  theme_classic() +
  theme(strip.background = element_blank())
mass.removed.p

erosion.p <- ggarrange(area.grazed.p, mass.removed.p, ncol = 2, nrow = 1, labels = c("a", "b"), 
                       font.label = list(size = 10, color = "black"))
erosion.p

ggsave("Figures/Parasites/erosion.png", plot = erosion.p,
       width = 6.5, height = 3, dpi = 300)
```

