---
title: "Parasites"
author: "Joshua Manning"
date: "`r Sys.Date()`"
output: html_document
---

Load packages

```{r}
#Data wrangling
library(plyr)
library(dplyr) 
library(tidyr) 
library(tibble) 
library(lubridate) #Dealing with time issues

#Movement and spatial analyses
library(adehabitatHR) #Home range analyses
library(adehabitatLT)
library(sf)  #Simple features
library(sp)  #This will be retired soon, but the code using sp objects can be shifted to sf objects easily enough
library(nngeo) #For function st_remove_holes

#Statistical analyses
library(car) #ANOVA
library(glmmTMB) #For linear, generalized linear, and generalized linear mixed modeling
library(performance)
library(DHARMa) #Checking model assumptions
library(emmeans) #marginal means of mixed models

#Data visualization
library(ggplot2) #Tidyverse visualization package
library(ggpubr) #For ggarrange() etc.
library(extrafont) #Change plot fonts

#Misc
library(conflicted) #Resolved conflicts
```

Resolve conflicts

```{r}
conflict_prefer("rename", "dplyr")
conflict_prefer("group_by", "dplyr")
conflict_prefer("filter", "dplyr")
conflict_prefer("summarise", "dplyr")
conflict_prefer("select", "dplyr")
conflict_prefer("mutate", "dplyr")
conflict_prefer("count", "dplyr")
conflict_prefer("contr.sum", "stats")
conflict_prefer("id", "adehabitatLT")
```


## Load data


Read in parasite data

```{r eval = F}
parasites <- read.csv("Data/parasites_total.csv") %>%
  separate(File.Name, c("Site", "Species", "Phase", "Date", "EndTime", "Vid"), sep = "_") %>%
  select(-Vid, Body.Part) %>%
  rename(BS1 = BS_Reviewer.1,
         BS2 = BS_Reviewer.2,
         WS1 = WS_Reviewer.1,
         WS2 = WS_Reviewer.2) %>%
  mutate(BS = round((BS1+BS2)/2, 0),
         WS = round((WS1+WS2)/2, 0),
         Total_load = BS + WS) %>%
  select(-c(BS1, BS2, WS1, WS2, Body.Part))
```


Read in home range/core use sizes and contours for mapping

```{r eval = F}
hr.size <- read.csv("ProcessedData/Full_HRs.csv")

AQ95 <- st_read("ProcessedData/aq2021.mkde95.shp") 

AQ50 <- st_read("ProcessedData/aq2021.mkde50.shp")

IV95 <- st_read("ProcessedData/iv2021.mkde95.shp")

IV50 <- st_read("ProcessedData/iv2021.mkde50.shp")

# Determine centroids of home ranges for mapping infection
AQcent <- st_centroid(AQ95)
IVcent <- st_centroid(IV95)
```


Read in behavioral observation annotations.

```{r eval = F}
bhav <- read.csv("Data/behave2021_updated.csv")

# Calculate observation times
follow.start <- bhav %>%
  filter(Behavior == "START/STOP") %>%
  filter(Status == "START") %>%
  rename(Start = "Time") %>%
  select(ID, Start)
n_distinct(follow.start) #86

follow.stop <- bhav %>%
  filter(Behavior == "START/STOP") %>%
  filter(Status == "STOP") %>%
  rename(Stop = "Time") %>%
  select(ID, Stop)
n_distinct(follow.stop) #86

follow.time <- left_join(follow.stop, follow.start) %>%
  mutate(Follow.Time = (Stop - Start)/60) %>%
  select(ID, Follow.Time) %>%
  separate(ID, c("Site", "Species", "Phase", "Date", "EndTime"), sep = "_")


# Format behavioral data - create time stamps for each behavior

# Start by creating a new data frame with the start times (time on watch in video) for each video observation
starts <- bhav %>%
  filter(Behavior == "Watch Time") %>%
  select(ID, Time, Modifier.1) %>%
  rename(WatchTime = Time, 
         Watch = Modifier.1)

starts$Watch <- as.POSIXct(starts$Watch, format="%H%M%S")
starts$Watch <- format(starts$Watch, "%H:%M:%S")

library(chron)

beh.fin <- plyr::join(bhav, starts, by = "ID") %>%
  separate(ID, c("Site", "Species", "Phase", "Date", "EndTime"), sep = "_", remove = F) %>%
  select(-Media.file.path, -Total.length, -FPS, -Subject, -Behavioral.category, -Comment)

beh.fin$Time <- times(beh.fin$Time / (24 * 60 * 60))
beh.fin$WatchTime <- times(beh.fin$WatchTime / (24 * 60 * 60))

beh.fin$ActualTime <- beh.fin$Watch + (beh.fin$Time - beh.fin$WatchTime)
```


Next, combine the date and actual time columns and make it POSIXct

```{r eval = F}
beh.fin$Date <- as.Date(beh.fin$Date)

beh.fin <- beh.fin %>% unite("time", c("Date", "ActualTime"), sep = " ", remove = F)

beh.fin$time <- as.POSIXct(strptime(as.character(beh.fin$time), "%Y-%m-%d %H:%M:%S"))

#Convert the actual times to UTC by adding 4 hours (EST is UTC-4 in spring/summer)
beh.fin$time <- beh.fin$time + lubridate::hours(4)

behavior <- beh.fin %>%
  select(-Site, -Species, -Phase, -Date, -EndTime, -Watch, -WatchTime)
```


Compute bite rates and get cleaning time

```{r eval = F}
bites <- behavior %>%
  filter(Behavior == "Bite") %>%
  group_by(ID) %>%
  summarise(N_bites = n()) %>%
  ungroup() %>%
  separate(ID, c("Site", "Species", "Phase", "Date", "EndTime"), sep = "_")

conflicts_prefer(dplyr::arrange)
conflicts_prefer(dplyr::lag)

# cleaning <- behavior %>%
#   filter(Behavior == "Cleaning") %>%
#   arrange(ID, time) %>%
#   mutate(Duration = time - lag(time)) %>%
#   filter(Status == "STOP") %>%
#   group_by(ID) %>%
#   summarise(N_clean = n(), 
#             Dur_clean = as.numeric(sum(Duration))) %>%
#   ungroup() %>%
#   separate(ID, c("Site", "Species", "Phase", "Date", "EndTime"), sep = "_")

interact <- behavior %>%
  filter(Behavior == "Parrotfish") %>%
  arrange(ID, time) %>%
  mutate(Duration = time - lag(time)) %>%
  filter(Status == "STOP") %>%
  group_by(ID) %>%
  summarise(N_int = n(), 
            Dur_int = as.numeric(sum(Duration))) %>%
  ungroup() %>%
  separate(ID, c("Site", "Species", "Phase", "Date", "EndTime"), sep = "_")
```


Merge behavioral and spatial data with parasite loads

```{r eval = F}
centroids <- rbind(AQcent, IVcent) %>% select(-ID)

final.parasites <- centroids %>%
  left_join(bites) %>%
  left_join(cleaning) %>%
  left_join(interact) %>%
  left_join(parasites) %>%
  left_join(follow.time) %>%
  filter(!is.na(Total_load)) %>%
  mutate(N_clean = ifelse(is.na(N_clean), 0, N_clean),
         Dur_clean = ifelse(is.na(Dur_clean), 0, Dur_clean))

st_write(final.parasites, "ProcessedData/final.parasites.shp") # Save as a shapefile
```


## Read in full data set

```{r}
final.parasites <- st_read("ProcessedData/final.parasites.shp")
```


## Map the infections

```{r}
AQ_SPA_SCT_HR <- ggplot() +
  geom_sf(data = final.parasites %>% filter(Site == "AQ"), 
          aes(color = Species, size = Total_load), linewidth = 0.5, alpha = 0.2) +
  coord_sf(datum = st_crs(32619)) +
  theme_classic() +
  scale_x_continuous("Easting (m)", limits = c(577630, 577720), breaks = c(577635, 577675, 577715)) +
  scale_y_continuous("Northing (m)", limits = c(1337440, 1337560), 
                     breaks = c(1337420, 1337460, 1337500, 1337540, 1337580)) + 
  theme(axis.title = element_text(size = 12, color = "black"),
        axis.text = element_text(size = 10, color = "black"),
        panel.border = element_rect(color = "black", fill = NA, linewidth = 2)) +
  labs(color = "Species", size = "Load") +
  scale_color_manual(labels = c("Princess", "Redband"), values = c("navy", "darkred")) +
  annotate("text", x = 577705, y = 1337555, label = "Aquarius") +
  guides(color = guide_legend(order = 1))
AQ_SPA_SCT_HR

#Save figure
ggsave("Figures/Parasites/AQ_parasiteloads.png", plot = AQ_SPA_SCT_HR,
       width = 4, height = 4, dpi = 300)

IV_SPA_SCT_HR <- ggplot() +
  geom_sf(data = final.parasites %>% filter(Site == "IV"), 
          aes(color = Species, size = Total_load), linewidth = 0.5, alpha = 0.2) +
  coord_sf(datum = st_crs(32619)) +
  theme_classic() +
  scale_x_continuous("Easting (m)", limits = c(578130, 578195), breaks = c(578140, 578165, 578190)) +
  scale_y_continuous("Northing (m)", limits = c(1335260, 1335345), 
                     breaks = c(1335265, 1335290, 1335315, 1335340)) +
  theme(axis.title = element_text(size = 12, color = "black"),
        axis.text = element_text(size = 10, color = "black"),
        panel.border = element_rect(color = "black", fill = NA, linewidth = 2)) +
  labs(color = "Species", size = "Load") +
  scale_color_manual(labels = c("Princess", "Redband"), values = c("navy", "darkred"))  +
  annotate("text", x = 578185, y = 1335340, label = "Invisibles") +
  guides(color = guide_legend(order = 1))
IV_SPA_SCT_HR

ggsave("Figures/Parasites/IV_parasiteloads.png", plot = IV_SPA_SCT_HR,
       width = 4, height = 4, dpi = 300)
```


Bites, parrotfish interactions, and cleaning as a function of infection

```{r}
# Bites

spa.final.parasites <- final.parasites %>%
  filter(Species == "Spaurofrenatum")

bite.para.m <- glmmTMB(data = spa.final.parasites, N_bites ~ log(Total_load+1) + offset(log(Follow.Time)), family = "gaussian")
test.bite.para <- simulateResiduals(fittedModel = bite.para.m, n = 250, plot = T)
summary(bite.para.m)

bites.p <- ggplot(data = spa.final.parasites, aes(x = log(Total_load+1), y = N_bites/Follow.Time, color = Species)) +
  geom_point(color = "darkred", alpha = 0.2) +
  geom_smooth(method = "lm", color = "darkred", fill = "darkred", alpha = 0.1) +
  theme_classic() +
  labs(x = "log(Parasite Load + 1)", y = expression(paste("Bites min" ^-1))) +
  annotate("text", x = 3.5, y = 11.8, label = "log(Parasite Load+1)") +
  annotate("text", x = 3.5, y = 11.5, label = "italic(p) == 0.16", parse = T)
bites.p

ggsave("Figures/Parasites/Spa_bites.png", plot = bites.p,
       width = 4, height = 4, dpi = 300)

# Parrotfish interactions

# int.para.m <- glmmTMB(data = final.parasites, Dur_int ~ Species + log(Total_load+1) + 
#                          offset(log(Follow.Time)), family = "gaussian")
# test.int.para <- simulateResiduals(fittedModel = int.para.m, n = 250, plot = T)
# summary(int.para.m)

int.para.m <- glmmTMB(data = spa.final.parasites, Dur_int ~ log(Total_load+1) +
                         offset(log(Follow.Time)), family = "gaussian")
test.int.para <- simulateResiduals(fittedModel = int.para.m, n = 250, plot = T)
summary(int.para.m)

icount.para.m <- glmmTMB(data = spa.final.parasites, N_int ~ log(Total_load+1) +
                         offset(log(Follow.Time)), family = "gaussian")
test.icount.para <- simulateResiduals(fittedModel = icount.para.m, n = 250, plot = T)
summary(icount.para.m)

# int.dur.p <- ggplot(data = final.parasites, aes(x = log(Total_load+1), y = Dur_int)) +
#   geom_point(aes(color = Species), alpha = 0.2) +
#   geom_smooth(method = "lm", color = "black", fill = "black", alpha = 0.1) +
#   scale_color_manual(labels = c("Princess", "Redband"), values = c("navy", "darkred")) +
#   theme_classic() +
#   labs(x = "log(Parasite Load + 1)", y = "Total Interaction Duration (s)") +
#   annotate("text", x = 2, y = 136, label = "log(Parasite Load+1)") +
#   annotate("text", x = 2, y = 130, label = "italic(p) == 0.03", parse = T)
# int.dur.p

int.count.p <- ggplot(data = spa.final.parasites, aes(x = log(Total_load+1), y = N_int)) +
  geom_point(color = "darkred", alpha = 0.2) +
  geom_smooth(method = "lm", color = "darkred", fill = "darkred", alpha = 0.1) +
  theme_classic() +
  labs(x = "log(Parasite Load + 1)", y = "Interaction Counts")
int.count.p

int.dur.p <- ggplot(data = spa.final.parasites, aes(x = log(Total_load+1), y = Dur_int)) +
  geom_point(color = "darkred", alpha = 0.2) +
  geom_smooth(method = "lm", color = "darkred", fill = "darkred", alpha = 0.1) +
  theme_classic() +
  labs(x = "log(Parasite Load + 1)", y = "Total Interaction Duration (s)") +
  annotate("text", x = 2, y = 136, label = "log(Parasite Load+1)") +
  annotate("text", x = 2, y = 130, label = "italic(p) == 0.428", parse = T)
int.dur.p

ggsave("Figures/Parasites/int_duration.png", plot = int.dur.p,
       width = 5, height = 4, dpi = 300)

#Home range area

# hr.para.m <- glmmTMB(data = final.parasites, area ~ Species*log(Total_load+1) + 
#                        offset(log(Follow.Time)), family = "gaussian")
# test.hr.para <- simulateResiduals(fittedModel = hr.para.m, n = 250, plot = T)
# summary(hr.para.m)

hr.para.m <- glmmTMB(data = spa.final.parasites, area ~ log(Total_load+1) + 
                       offset(log(Follow.Time)), family = "gaussian")
test.hr.para <- simulateResiduals(fittedModel = hr.para.m, n = 250, plot = T)
summary(hr.para.m)

# hr.p <- ggplot(data = final.parasites, aes(x = log(Total_load+1), y = area, color = Species)) +
#   geom_point(alpha = 0.2) +
#   geom_smooth(method = "lm", aes(fill = Species), alpha = 0.1) +
#   theme_classic() +
#   scale_color_manual(labels = c("Princess", "Redband"), values = c("navy", "darkred")) +
#   scale_fill_manual(labels = c("Princess", "Redband"), values = c("navy", "darkred")) +
#   labs(x = "log(Parasite Load + 1)", y = expression(paste("Home Range m" ^2))) +
#   annotate("text", x = 2, y = 355, label = "Species:log(Parasite Load+1)") +
#   annotate("text", x = 2, y = 343, label = "italic(p) == 0.002", parse = T)
# hr.p

hr.p <- ggplot(data = spa.final.parasites, aes(x = log(Total_load+1), y = area)) +
  geom_point(color = "darkred", alpha = 0.2) +
  geom_smooth(method = "lm", color = "darkred", fill = "darkred", alpha = 0.1) +
  theme_classic() +
  labs(x = "log(Parasite Load + 1)", y = expression(paste("Home Range Area" ^2))) +
  annotate("text", x = 2, y = 355, label = "log(Parasite Load+1)") +
  annotate("text", x = 2, y = 343, label = "italic(p) == 0.033", parse = T)
hr.p

ggsave("Figures/Parasites/homerange.png", plot = hr.p,
       width = 5, height = 4, dpi = 300)
```


