---
title: "Processing New Bite Data - Sc taeniopterus"
author: "Joshua Manning"
date: "`r Sys.Date()`"
output: html_document
---

##Load Packages##

Load packages
Not all are used. Some are remnants of prior coding and more packages may be added later.

```{r}
#Reading in, handling, cleaning data.

library(tidyr) #data handling
library(plyr)
library(dplyr) #data wrangling
library(tibble)
library(lubridate)
library(purrr)

# library(adehabitatLT)

#Statistical analyses

library(car)

#Plotting and mapping

library(ggplot2) # tidyverse vis package
library(ggpubr) #for ggarrange() etc.
library(gridExtra) #has a function for comparing ggplot plots side by side.

#Dealing with conflicts

library(conflicted)
```

Resolve conflicts

```{r}
conflict_prefer("rename", "dplyr")
conflict_prefer("group_by", "dplyr")
conflict_prefer("filter", "dplyr")
conflict_prefer("summarise", "dplyr")
conflict_prefer("select", "dplyr")
conflict_prefer("mutate", "dplyr")
conflict_prefer("count", "dplyr")
conflict_prefer("arrange", "dplyr")
conflict_prefer("lag", "dplyr")
conflict_prefer("contr.sum", "stats")
# conflict_prefer("id", "adehabitatLT")
```

## Read in all CSV files - Initial

In the new data set:

AQ_Sctaeniopterus_TP_2021-06-14_135125: The file name and video name in file path matched, but Observation id was wrong. So, Iv changed the Observation id in the raw file. 

For AQ_Sctaeniopterus_TP_2021-06-14_104539 there are no bites recorded

```{r}
files <- dir(path = "Data/bites_sct_new", pattern = "\\.csv", full.names = T)
out <- lapply(files, function(x) read.csv(x))
names(out) <- basename(files)

full <- lapply(out, function(x) bind_rows(x, .id = "column_label"))

# Bind rows and then reformat everything so that it matches the behave2021 dataset
full.df <- bind_rows(full, .id="column_label") %>%
  filter(Behavior.type == "POINT" & Behavior == "Bite") %>%
  select(-column_label, -Observation.date, -Description, -Stop..s., -Comment.stop, -Duration..s.) %>%
  rename(ID = Observation.id,
         Time = Start..s.,
         Comment = Comment.start,
         Status = Behavior.type,
         Media.file.path = Media.file) %>%
  separate(Modifiers, c("Modifier.1", "Modifier.2", "Modifier.3", "Modifier.4", "Modifier.5"), sep = "[|]") %>%
  select(ID, Time, Media.file.path, Total.length, FPS, Subject, Behavior, Behavioral.category, 
         Modifier.1, Modifier.2, Modifier.3, Modifier.4, Modifier.5, Comment, Status)
  
  
# rbind to behave2021 and then arrange by ID and Time to order bites, etc.
bhav <- read.csv("Data/behave2021.csv") %>%
  rbind(full.df) %>%
  arrange(ID, Time)

write.csv(bhav, "Data/behave2021_updated.csv", row.names = F)
```
